---
title: "Step 07: Check Stability of ES in Total Sample"
output:
  html_document:
    df_print: paged
---

This R Notebook checks stability of ES in dimensional analyses by running models in randomly selected samples between n=100 and n=600 100 times each. 

------------------------------
Set Up
------------------------------

First, install necessary packages.
```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(lm.beta)
library(ggpubr)
library(bayesbio)
library(mde)
library(lavaan) 
library(knitr)
```

Specify that select function should be pulled from dplyr
```{r}
select <- dplyr::select
recode <- dplyr::recode
```

Next, log into PennBox, and set working directory the ABCD directory.
```{r}
box_auth()

box_setwd('167848222541')
```

Load in dimensional data:
```{r}
all_dimensional_data<-box_read('1438646812672', fread=TRUE)
```

Read in biological data 
```{r}
bio<-box_read('1301072938826', fread=TRUE)
bio<-bio[,c(2:5, 11)]
bio$participant<-gsub('sub-NDARINV','NDAR_INV',bio$participant)
ga<-box_read('1277090709031', fread=TRUE)
bmi<-box_read('1441672468205', fread=TRUE)%>%
  select(subjectkey, bmi)

bio<- merge(bmi,bio , by.y='participant', by.x='subjectkey', all.x=T)
```

make a group variable (adolescents born at less than 33 weeks, 34–35 weeks, 36 weeks, 37–39 weeks, and 40 weeks of gestation)
```{r}
ga_clean<-as_tibble(ga)%>%
  select(src_subject_id, eventname, birth_weight_lbs, birth_weight_oz, devhx_12a_p, devhx_12_p)%>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  mutate(birth_weight_oz=birth_weight_oz/16)%>%
  mutate(bw= birth_weight_lbs +birth_weight_oz)%>%
  recode_na_as(subset_cols= 'devhx_12_p', value=0)%>%
  recode_as_na(subset_cols= 'devhx_12a_p', value=999)%>%
  mutate(ga= 40-devhx_12_p)%>%
  mutate(ga_group = case_when(
      ga == 40 ~ "1",
      ga >=37 & ga <=39  ~ "2",
      ga == 36 ~ "3", 
      ga >=34 & ga <=35 ~ "4", 
      ga <=33 ~ "5"
    ))%>%
  select(src_subject_id, ga_group)

bio<- merge(bio, ga_clean, by.x='subjectkey', by.y='src_subject_id')
```

Read in CBCL data that will be used to make the CU traits measure (expand by timepoint, select q26). 
```{r}
cbcl<-box_read('1277090142488')
cbcl<- as_tibble(cbcl)%>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  select(src_subject_id, cbcl_scr_dsm5_depress_r, cbcl_scr_dsm5_anxdisord_r, 
                     cbcl_scr_dsm5_adhd_r, cbcl_scr_dsm5_opposit_r,
                     cbcl_scr_dsm5_conduct_r, cbcl_scr_dsm5_somaticpr_r)
```

Read in Cognitive Data 
```{r}
cog_data<-box_read('1022619576971', fread=TRUE)
cog_data<-as_tibble(cog_data)%>%
  slice(2:n()) %>% #drop the first row, which contains the variable definitions
  dplyr::select(-collection_id,-abcd_tbss01_id,-dataset_id,-interview_date) %>% 
  dplyr::select_if(~!(all(is.na(.)) | all(. == ""))) %>% #get rid of totally empty columns
  mutate(across(everything(), ~ifelse(.=="", NA, as.character(.)))) #recode blank rows as "NA" 

cog_data_short<- cog_data %>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  dplyr::select(ends_with(c("subjectkey", "uncorrected")))

```

Merge:
```{r}
all_data<- merge(all_dimensional_data, bio, by='subjectkey')
all_data<- merge(all_data, cog_data_short, by='subjectkey')
all_data<- merge(all_data, cbcl, by.x='subjectkey', by.y='src_subject_id')
```

------------------------------
Run models 
------------------------------

Now, specify models to be run various times with different samples: 
```{r}
bw_model<- 'bw ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income'
cog_model<- 'nihtbx_picvocab_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income'
cbcl_model<- 'cbcl_scr_dsm5_adhd_r ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income'
```

```{r, results = 'hide', message = FALSE, warning = FALSE}
set.seed(12345)

# Initialize parameters
sample_sizes <- seq(100, 6000, by=100)  # Define your sample sizes
n_runs <- 100  # Number of repetitions
effect_sizes <- data.frame()  # Create an empty data frame to store results

# Main loop to run the model
for (sample_size in sample_sizes) {
  for (run in 1:n_runs) {
    # Sample the data
    sampled_data <- all_data[sample(1:nrow(all_data), sample_size, replace = TRUE), ]
    
    # Fit the linear model
    fit <- sem(bw_model, data = sampled_data)
    
    # Extract effect sizes (e.g., standardized estimates)
    effect_size <- parameterEstimates(fit, standardized = TRUE)
    
    # Directly extract the effect size for predictor1 (modify "predictor1" as needed)
    predictor_effect <- filter(effect_size, lhs == "bw" & rhs == "GMV")
    
     # Store the result
    effect_sizes <- rbind(effect_sizes, data.frame(sample_size = sample_size, effect_size_value = predictor_effect))
  }
}

```

```{r}
# Plotting
bio_plot<- ggplot(effect_sizes, aes(x = sample_size, y = effect_size_value.std.all)) +
  geom_point(color="#f8766d7f", alpha=.25)+
  geom_smooth(method = "loess", se = TRUE, level=.95, color = "#F8766D", fill="#F8766D") +  # Smooth line with confidence interval
  labs(x = "Sample Size",
       y = "Effect Size (cGM)") +
  theme_minimal()

bio_plot
```

```{r, results = 'hide', message = FALSE, warning = FALSE}
set.seed(12345)

# Initialize parameters
sample_sizes <- seq(100, 6000, by=100)  # Define your sample sizes
n_runs <- 100  # Number of repetitions
effect_sizes <- data.frame()  # Create an empty data frame to store results

# Main loop to run the model
for (sample_size in sample_sizes) {
  for (run in 1:n_runs) {
    # Sample the data
    sampled_data <- all_data[sample(1:nrow(all_data), sample_size, replace = TRUE), ]
    
    # Fit the linear model
    fit <- sem(cbcl_model, data = sampled_data)
    
    # Extract effect sizes (e.g., standardized estimates)
    effect_size <- parameterEstimates(fit, standardized = TRUE)
    
    # Directly extract the effect size for predictor1 (modify "predictor1" as needed)
    predictor_effect <- filter(effect_size, lhs == "cbcl_scr_dsm5_adhd_r" & rhs == "GMV")
    
     # Store the result
    effect_sizes <- rbind(effect_sizes, data.frame(sample_size = sample_size, effect_size_value = predictor_effect))
  }
}

```


```{r}
# Plotting
cbcl_plot<- ggplot(effect_sizes, aes(x = sample_size, y = effect_size_value.std.all)) +
  geom_point(color='#00ba383e', alpha=.25)+
  geom_smooth(method = "loess", se = TRUE, level=.95, color = "#00BA38", fill="#00BA38") +  # Smooth line with confidence interval
  labs(x = "Sample Size",
       y = "Effect Size (cGM)") +
  theme_minimal()

cbcl_plot
```


```{r, results = 'hide', message = FALSE, warning = FALSE}
set.seed(12345)

# Initialize parameters
sample_sizes <- seq(100, 6000, by=100)  # Define your sample sizes
n_runs <- 100  # Number of repetitions
effect_sizes <- data.frame()  # Create an empty data frame to store results

# Main loop to run the model
for (sample_size in sample_sizes) {
  for (run in 1:n_runs) {
    # Sample the data
    sampled_data <- all_data[sample(1:nrow(all_data), sample_size, replace = TRUE), ]
    
    # Fit the linear model
    fit <- sem(cog_model, data = sampled_data)
    
    # Extract effect sizes (e.g., standardized estimates)
    effect_size <- parameterEstimates(fit, standardized = TRUE)
    
    # Directly extract the effect size for predictor1 (modify "predictor1" as needed)
    predictor_effect <- filter(effect_size, lhs == "nihtbx_picvocab_uncorrected" & rhs == "GMV")
    
     # Store the result
    effect_sizes <- rbind(effect_sizes, data.frame(sample_size = sample_size, effect_size_value = predictor_effect))
  }
}

```

```{r}
# Plotting
cog_plot<- ggplot(effect_sizes, aes(x = sample_size, y = effect_size_value.std.all)) +
  geom_point(color='#619cff5f', alpha=.25) +
  geom_smooth(method = "loess", se = TRUE, level=.95, color = "#619CFF", fill="#619CFF") +  # Smooth line with confidence interval
  labs(x = "Sample Size",
       y = "Effect Size (cGM)") +
  theme_minimal()
  
cog_plot 
```

Altogether:
```{r}
curves<- ggarrange(bio_plot, cog_plot, cbcl_plot, nrow=1, ncol=3)

curves
```
