---
title: "Topography Matching Notebook Step 2"
output:
  html_document:
    df_print: paged
---

This R Notebook runs multivariate multiple regression to model the effects of regional GMV on biological outcomes using dimensional, tail sampled, and propensity matched modeling strategies. 

-----------------------------------
Set Up
-----------------------------------
```{r}
set.seed(12345)
```

First, install necessary packages.

```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(lm.beta)
library(ggpubr)
library(bayesbio)
library(viridis)
library(ggExtra)
library(dichromat)
library(lavaan)
library(dplyr)
library(stringr)
```

Specify color palette

```{r}
custom_colors <- colorRampPalette(c("blue","darkturquoise","white", "yellow", "red"))
```

Specify that select function should be pulled from dplyr

```{r}
select <- dplyr::select
recode <- dplyr::recode
rename <- dplyr::rename
mutate <- dplyr::mutate
revalue <- plyr::revalue
```

Next, log into PennBox, and set working directory the ABCD directory.

```{r}
box_auth()

box_setwd('167848222541')
```

Load in matched network data:
```{r}
GMV_test_data<-box_read('1438677748369', fread=TRUE)
```

Read in outcome data 
```{r}
bio<-box_read('1301072938826', fread=TRUE)
bio<-bio[,c(2:5, 11)]
bio$participant<-gsub('sub-NDARINV','NDAR_INV',bio$participant)
ga<-box_read('1277090709031', fread=TRUE)
bmi<-box_read('1441672468205', fread=TRUE)%>%
  select(subjectkey, bmi)
```
calculate gestational age and recalc birthday weight in lbs and oz

make a group variable (adolescents born at less than 33 weeks, 34–35 weeks, 36 weeks, 37–39 weeks, and 40 weeks of gestation)
```{r}
ga_clean<-as_tibble(ga)%>%
  select(src_subject_id, eventname, birth_weight_lbs, birth_weight_oz, devhx_12a_p, devhx_12_p)%>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  mutate(birth_weight_oz=birth_weight_oz/16)%>%
  mutate(bw= birth_weight_lbs +birth_weight_oz)%>%
  recode_na_as(subset_cols= 'devhx_12_p', value=0)%>%
  recode_as_na(subset_cols= 'devhx_12a_p', value=999)%>%
  mutate(ga= 40-devhx_12_p)%>%
  mutate(ga_group = case_when(
      ga == 40 ~ "1",
      ga >=37 & ga <=39  ~ "2",
      ga == 36 ~ "3", 
      ga >=34 & ga <=35 ~ "4", 
      ga <=33 ~ "5"
    ))%>%
  mutate(ga_group = as.numeric(ga_group))
```

And read in regional data, make a list of all the predictor names: 
```{r}
regional_data<- box_read('1558667085128', fread=TRUE)
regional_data$participant<-gsub('sub-NDARINV','NDAR_INV',regional_data$participant)

regional_predictors<- colnames(regional_data)[4:71]
```

merge:
```{r}
GMV_test_data<-merge(GMV_test_data, bmi, by='subjectkey')
GMV_test_data<-merge(GMV_test_data, ga_clean, by.x='subjectkey', by.y='src_subject_id')
GMV_test_data<- merge(GMV_test_data, regional_data, by.x='subjectkey', by.y='participant')
```

```{r}
psych::describe(GMV_test_data)
```

Now load in unmatched network data: 
```{r}
unmatched_GMV_data<-box_read('1438648430018', fread=TRUE)
```

merge:
```{r}
GMV_test_data2<-merge(unmatched_GMV_data, bmi, by='subjectkey')
GMV_test_data2<-merge(GMV_test_data2, ga_clean, by.x='subjectkey', by.y='src_subject_id')
GMV_test_data2<- merge(GMV_test_data2, regional_data, by.x='subjectkey', by.y='participant')
```

```{r}
#psych::describe(GMV_test_data2)
```

Load in dimensional network data, merge: 
```{r}
all_dimensional_data<-box_read('1438646812672', fread=TRUE)

all_dimensional_data<- merge(all_dimensional_data, bmi, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)
all_dimensional_data<- merge(all_dimensional_data, ga_clean, by.x='subjectkey', by.y='src_subject_id')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)
all_dimensional_data<- merge(all_dimensional_data, regional_data, by.x='subjectkey', by.y='participant')
```
```{r}
psych::describe(all_dimensional_data)
```

-----------------------------------
Specify Models, Functions
-----------------------------------

Write out a template for our dependent variables: 
```{r}
model_template<- 
'
bw ~ {predictor} + age + sex.x + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
ga_group ~ {predictor} + age + sex.x + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
bmi ~ {predictor} + age + sex.x + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income

bw ~~ ga_group
ga_group ~~ bmi
bmi ~~ bw
'
```

Fit model with each of 68 predictors in matched data:
```{r}
fit_model <- function(predictor) {
  model <- gsub("\\{predictor\\}", predictor, model_template)
  fit <- sem(model, data = GMV_test_data)
  estimates <- parameterEstimates(fit, standardized = TRUE)
  results <- estimates %>%
    filter(op == "~" & lhs %in% c("bw",
                                  "ga_group", 
                                  "bmi") & rhs %in% c(predictor, 'age', 'sex.x', 'site_id', 'puberty_stage',
                                                                             'ethnicity', 'race_3', 'parent_education', 
                                                                             'combined_income')) %>%
    select(lhs, rhs, est, se, std.all, pvalue) %>%
    rename(dependent = lhs, 
           beta = std.all, 
           p.value = pvalue)%>%
    mutate(predictor = rep(c(predictor, 'age', 'sex', 'site', 'puberty','ethnicity', 'race', 'parent_education', 'combined_income'),
                           length.out = n()))
  
    return(results)
}
```

Fit model with each of 68 predictors in tail sampled data: 
```{r}
fit_model2 <- function(predictor) {
  model <- gsub("\\{predictor\\}", predictor, model_template)
  fit <- sem(model, data = GMV_test_data2)
  estimates <- parameterEstimates(fit, standardized = TRUE)
  all_vars <- c(predictor, "age", "sex.x", "site_id", "puberty_stage", 
                "ethnicity", "race_3", "parent_education", "combined_income")
  results <- estimates %>%
    filter(op == "~" & lhs %in% c("bw",
                                  "ga_group", 
                                  "bmi") & rhs %in% c(predictor, 'age', 'sex.x', 'site_id', 'puberty_stage',
                                                                             'ethnicity', 'race_3', 'parent_education', 
                                                                             'combined_income')) %>%
    select(lhs, rhs, est, se, std.all, pvalue) %>%
    rename(dependent = lhs, 
           beta = std.all, 
           p.value = pvalue)%>%
    mutate(predictor = rep(c(predictor, 'age', 'sex', 'site', 'puberty','ethnicity', 'race', 'parent_education', 'combined_income'),
                           length.out = n()))
  
    return(results)
}
```

Fit model with each of 68 predictors in dimensional data: 
```{r}
fit_model3 <- function(predictor) {
  model <- gsub("\\{predictor\\}", predictor, model_template)
  fit <- sem(model, data = all_dimensional_data)
  estimates <- parameterEstimates(fit, standardized = TRUE)
  all_vars <- c(predictor, "age", "sex.x", "site_id", "puberty_stage", 
                "ethnicity", "race_3", "parent_education", "combined_income")
  results <- estimates %>%
    filter(op == "~" & lhs %in% c("bw",
                                  "ga_group", 
                                  "bmi") & rhs %in% c(predictor, 'age', 'sex.x', 'site_id', 'puberty_stage',
                                                                             'ethnicity', 'race_3', 'parent_education', 
                                                                             'combined_income')) %>%
    select(lhs, rhs, est, se, std.all, pvalue) %>%
    rename(dependent = lhs, 
           beta = std.all, 
           p.value = pvalue)%>%
    mutate(predictor = rep(c(predictor, 'age', 'sex', 'site', 'puberty','ethnicity', 'race', 'parent_education', 'combined_income'),
                           length.out = n()))
  
    return(results)
}
```

-----------------------------------
Evaluate Fit
-----------------------------------

Matched data:
```{r}
results <- lapply(regional_predictors, fit_model) %>% bind_rows()
```

FDR correct: 
```{r}
results<- results%>%
   mutate(ps_fdr= (p.adjust.nlp(p.value, method='fdr', n=612)))
```

Tail sampled data: 
```{r}
results2 <- lapply(regional_predictors, fit_model2) %>% bind_rows()
```

FDR correct: 
```{r}
results2<- results2%>%
   mutate(ps_fdr= (p.adjust.nlp(p.value, method='fdr', n=612)))
```

Dimensional Data: 
```{r}
results3 <- lapply(regional_predictors, fit_model3) %>% bind_rows()
```

FDR correct: 
```{r}
results3<- results3%>%
   mutate(ps_fdr= (p.adjust.nlp(p.value, method='fdr', n=612)))
```


-----------------------------------
Format Results
-----------------------------------

Format matched data: 
```{r}
#add significance
results_html<- results %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

results_html$formatted_raw_est <- paste0(round(results_html$est,2), ", (", round(results_html$se,2), ")")
results_html$formatted_std_est <- paste0(round(results_html$beta,2), results_html$significance)

results_html <- results_html %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)

#rename v's
results_html$dependent<- (factor(results_html$dependent, levels = c("bmi", "ga_group", "bw")))

results_html$predictor<-gsub('Transformed.q.wre','',results_html$predictor)

results_html$predictor<- revalue(results_html$predictor, c("rh.GM.bankssts" = "Right Banks of the superior temporal sulcus", 
                                                 "rh.GM.caudalanteriorcingulate" = "Right Caudal anterior cingulate cortex", 
                                                 "rh.GM.caudalmiddlefrontal" = "Right Caudal middle frontal gyrus", 
                                                 "rh.GM.cuneus" = "Right Cuneus cortex", 
                                                 "rh.GM.entorhinal" = "Right Entorhinal cortex", 
                                                 "rh.GM.fusiform" = "Right Fusiform gyrus", 
                                                 "rh.GM.inferiorparietal" = "Right Inferior parietal cortex", 
                                                 "rh.GM.inferiortemporal" = "Right Inferior temporal gyrus",
                                                 "rh.GM.isthmuscingulate" = "Right Isthmus Anterior Cingulate cortex", 
                                                 "rh.GM.lateraloccipital" = "Right Lateral occipital cortex", 
                                                 "rh.GM.lateralorbitofrontal" = "Right Lateral Orbitofrontal cortex", 
                                                 "rh.GM.lingual" = "Right Lingual gyrus", 
                                                 "rh.GM.medialorbitofrontal" = "Right Medial Orbitofrontal cortex", 
                                                 "rh.GM.middletemporal" = "Right Middle temporal gyrus", 
                                                 "rh.GM.parahippocampal" = "Right Parahippocampal gyrus", 
                                                 "rh.GM.paracentral" = "Right Paracentral lobule", 
                                                 "rh.GM.parsopercularis" = "Right Pars opercularis", 
                                                 "rh.GM.parsorbitalis" = "Right Pars orbitalis", 
                                                 "rh.GM.parstriangularis" = "Right Pars triangularis", 
                                                 "rh.GM.pericalcarine" = "Right Pericalcarine cortex", 
                                                 "rh.GM.postcentral" = "Right Postcentral gyrus", 
                                                 "rh.GM.posteriorcingulate" = "Right Posterior anterior cingulate cortex", 
                                                 "rh.GM.precentral" = "Right Precentral gyrus", 
                                                 "rh.GM.precuneus" = "Right Precuneus cortex", 
                                                 "rh.GM.rostralanteriorcingulate" = "Right Rostral anterior cingulate cortex", 
                                                 "rh.GM.rostralmiddlefrontal" = "Right Rostral middle frontal gyrus", 
                                                 "rh.GM.superiorfrontal" = "Right Superior frontal gyrus", 
                                                 "rh.GM.superiorparietal" = "Right Superior parietal cortex", 
                                                 "rh.GM.superiortemporal" = "Right Superior temporal gyrus", 
                                                 "rh.GM.supramarginal" = "Right Supramarginal gyrus", 
                                                 "rh.GM.frontalpole" = "Right Frontal pole", 
                                                 "rh.GM.temporalpole" = "Right Temporal pole", 
                                                 "rh.GM.transversetemporal" = "Right Transverse temporal cortex", 
                                                 "rh.GM.insula" = "Right Insula", 
                                                 "lh.GM.bankssts" = "Left Banks of the superior temporal sulcus", 
                                                 "lh.GM.caudalanteriorcingulate" = "Left Caudal anterior cingulate cortex", 
                                                 "lh.GM.caudalmiddlefrontal" = "Left Caudal middle frontal gyrus", 
                                                 "lh.GM.cuneus" = "Left Cuneus cortex", 
                                                 "lh.GM.entorhinal" = "Left Entorhinal cortex", 
                                                 "lh.GM.fusiform" = "Left Fusiform gyrus", 
                                                 "lh.GM.inferiorparietal" = "Left Inferior parietal cortex", 
                                                 "lh.GM.inferiortemporal" = "Left Inferior temporal gyrus",
                                                 "lh.GM.isthmuscingulate" = "Left Isthmus Anterior Cingulate cortex", 
                                                 "lh.GM.lateraloccipital" = "Left Lateral occipital cortex", 
                                                 "lh.GM.lateralorbitofrontal" = "Left Lateral Orbitofrontal cortex", 
                                                 "lh.GM.lingual" = "Left Lingual gyrus", 
                                                 "lh.GM.medialorbitofrontal" = "Left Medial Orbitofrontal cortex", 
                                                 "lh.GM.middletemporal" = "Left Middle temporal gyrus", 
                                                 "lh.GM.parahippocampal" = "Left Parahippocampal gyrus", 
                                                 "lh.GM.paracentral" = "Left Paracentral lobule", 
                                                 "lh.GM.parsopercularis" = "Left Pars opercularis", 
                                                 "lh.GM.parsorbitalis" = "Left Pars orbitalis", 
                                                 "lh.GM.parstriangularis" = "Left Pars triangularis", 
                                                 "lh.GM.pericalcarine" = "Left Pericalcarine cortex", 
                                                 "lh.GM.postcentral" = "Left Postcentral gyrus", 
                                                 "lh.GM.posteriorcingulate" = "Left Posterior anterior cingulate cortex", 
                                                 "lh.GM.precentral" = "Left Precentral gyrus", 
                                                 "lh.GM.precuneus" = "Left Precuneus cortex", 
                                                 "lh.GM.rostralanteriorcingulate" = "Left Rostral anterior cingulate cortex", 
                                                 "lh.GM.rostralmiddlefrontal" = "Left Rostral middle frontal gyrus", 
                                                 "lh.GM.superiorfrontal" = "Left Superior frontal gyrus", 
                                                 "lh.GM.superiorparietal" = "Left Superior parietal cortex", 
                                                 "lh.GM.superiortemporal" = "Left Superior temporal gyrus", 
                                                 "lh.GM.supramarginal" = "Left Supramarginal gyrus", 
                                                 "lh.GM.frontalpole" = "Left Frontal pole", 
                                                 "lh.GM.temporalpole" = "Left Temporal pole", 
                                                 "lh.GM.transversetemporal" = "Left Transverse temporal cortex", 
                                                 "lh.GM.insula" = "Left Insula"))

#expand cols (by predictor)
matched_results_html <- results_html %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  group_by(predictor, dependent, Estimate_Type) %>%
  mutate(dup_id = row_number()) %>%
  ungroup()%>%
  pivot_wider(
    names_from = c(dependent, Estimate_Type),
    values_from = Estimate,
    names_sep = "_",
    id_cols = c(predictor, dup_id)
  ) %>%
  select(-dup_id)

#create a variable that groups by predictor (ie: model) 
imaging_predictors <- matched_results_html$predictor[seq(1, length(matched_results_html$predictor), by = 9)]
matched_results_html$predictor_group <- rep(imaging_predictors, each = 9)

#add hemisphere variable 
matched_results_html <- matched_results_html %>%
  mutate(hemisphere = case_when(startsWith(as.character(predictor_group), "Left") ~ "Left", 
                                startsWith(as.character(predictor_group), "Right") ~ "Right"))%>%
  mutate(predictor = case_when(startsWith(as.character(predictor), "Left") ~ "Regional Predictor", 
                               startsWith(as.character(predictor), "Right") ~ "Regional Predictor", 
                               TRUE ~ predictor))

#Create a formatted regression table 
matched_regression_table <- matched_results_html %>%
  mutate(predictor = recode(predictor,"age" = "Age", "sex" = "Sex", "site" = "Site ID", "puberty" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))%>%
  gt(groupname_col = "predictor_group", rowname_col = "predictor") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using regional cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    bw_formatted_raw_est = "Raw", bw_formatted_std_est = "Standardized",
    ga_group_formatted_raw_est = "Raw", ga_group_formatted_std_est = "Standardized",
    bmi_formatted_raw_est = "Raw", bmi_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Birthweight",
    columns = c(bw_formatted_raw_est, bw_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Gestational Age",
    columns = c(ga_group_formatted_raw_est, ga_group_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Body Mass Index",
    columns = c(bmi_formatted_raw_est, bmi_formatted_std_est)
  ) %>%
  row_group_order(groups = unique(matched_results_html$predictor_group)) # Order models if necessary
```

Save the table as an HTML file
```{r}
matched_regression_table %>%
  gtsave("bio_regional_matched_table.html")
```

Format tails data: 
```{r}
#add significance
results_html2<- results2 %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

results_html2$formatted_raw_est <- paste0(round(results_html2$est,2), ", (", round(results_html2$se,2), ")")
results_html2$formatted_std_est <- paste0(round(results_html2$beta,2), results_html2$significance)

results_html2 <- results_html2 %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)

#rename v's
results_html2$dependent<- (factor(results_html2$dependent, levels = c("bmi", "ga_group", "bw")))

results_html2$predictor<-gsub('Transformed.q.wre','',results_html2$predictor)

results_html2$predictor<- revalue(results_html2$predictor, c("rh.GM.bankssts" = "Right Banks of the superior temporal sulcus", 
                                                 "rh.GM.caudalanteriorcingulate" = "Right Caudal anterior cingulate cortex", 
                                                 "rh.GM.caudalmiddlefrontal" = "Right Caudal middle frontal gyrus", 
                                                 "rh.GM.cuneus" = "Right Cuneus cortex", 
                                                 "rh.GM.entorhinal" = "Right Entorhinal cortex", 
                                                 "rh.GM.fusiform" = "Right Fusiform gyrus", 
                                                 "rh.GM.inferiorparietal" = "Right Inferior parietal cortex", 
                                                 "rh.GM.inferiortemporal" = "Right Inferior temporal gyrus",
                                                 "rh.GM.isthmuscingulate" = "Right Isthmus Anterior Cingulate cortex", 
                                                 "rh.GM.lateraloccipital" = "Right Lateral occipital cortex", 
                                                 "rh.GM.lateralorbitofrontal" = "Right Lateral Orbitofrontal cortex", 
                                                 "rh.GM.lingual" = "Right Lingual gyrus", 
                                                 "rh.GM.medialorbitofrontal" = "Right Medial Orbitofrontal cortex", 
                                                 "rh.GM.middletemporal" = "Right Middle temporal gyrus", 
                                                 "rh.GM.parahippocampal" = "Right Parahippocampal gyrus", 
                                                 "rh.GM.paracentral" = "Right Paracentral lobule", 
                                                 "rh.GM.parsopercularis" = "Right Pars opercularis", 
                                                 "rh.GM.parsorbitalis" = "Right Pars orbitalis", 
                                                 "rh.GM.parstriangularis" = "Right Pars triangularis", 
                                                 "rh.GM.pericalcarine" = "Right Pericalcarine cortex", 
                                                 "rh.GM.postcentral" = "Right Postcentral gyrus", 
                                                 "rh.GM.posteriorcingulate" = "Right Posterior anterior cingulate cortex", 
                                                 "rh.GM.precentral" = "Right Precentral gyrus", 
                                                 "rh.GM.precuneus" = "Right Precuneus cortex", 
                                                 "rh.GM.rostralanteriorcingulate" = "Right Rostral anterior cingulate cortex", 
                                                 "rh.GM.rostralmiddlefrontal" = "Right Rostral middle frontal gyrus", 
                                                 "rh.GM.superiorfrontal" = "Right Superior frontal gyrus", 
                                                 "rh.GM.superiorparietal" = "Right Superior parietal cortex", 
                                                 "rh.GM.superiortemporal" = "Right Superior temporal gyrus", 
                                                 "rh.GM.supramarginal" = "Right Supramarginal gyrus", 
                                                 "rh.GM.frontalpole" = "Right Frontal pole", 
                                                 "rh.GM.temporalpole" = "Right Temporal pole", 
                                                 "rh.GM.transversetemporal" = "Right Transverse temporal cortex", 
                                                 "rh.GM.insula" = "Right Insula", 
                                                 "lh.GM.bankssts" = "Left Banks of the superior temporal sulcus", 
                                                 "lh.GM.caudalanteriorcingulate" = "Left Caudal anterior cingulate cortex", 
                                                 "lh.GM.caudalmiddlefrontal" = "Left Caudal middle frontal gyrus", 
                                                 "lh.GM.cuneus" = "Left Cuneus cortex", 
                                                 "lh.GM.entorhinal" = "Left Entorhinal cortex", 
                                                 "lh.GM.fusiform" = "Left Fusiform gyrus", 
                                                 "lh.GM.inferiorparietal" = "Left Inferior parietal cortex", 
                                                 "lh.GM.inferiortemporal" = "Left Inferior temporal gyrus",
                                                 "lh.GM.isthmuscingulate" = "Left Isthmus Anterior Cingulate cortex", 
                                                 "lh.GM.lateraloccipital" = "Left Lateral occipital cortex", 
                                                 "lh.GM.lateralorbitofrontal" = "Left Lateral Orbitofrontal cortex", 
                                                 "lh.GM.lingual" = "Left Lingual gyrus", 
                                                 "lh.GM.medialorbitofrontal" = "Left Medial Orbitofrontal cortex", 
                                                 "lh.GM.middletemporal" = "Left Middle temporal gyrus", 
                                                 "lh.GM.parahippocampal" = "Left Parahippocampal gyrus", 
                                                 "lh.GM.paracentral" = "Left Paracentral lobule", 
                                                 "lh.GM.parsopercularis" = "Left Pars opercularis", 
                                                 "lh.GM.parsorbitalis" = "Left Pars orbitalis", 
                                                 "lh.GM.parstriangularis" = "Left Pars triangularis", 
                                                 "lh.GM.pericalcarine" = "Left Pericalcarine cortex", 
                                                 "lh.GM.postcentral" = "Left Postcentral gyrus", 
                                                 "lh.GM.posteriorcingulate" = "Left Posterior anterior cingulate cortex", 
                                                 "lh.GM.precentral" = "Left Precentral gyrus", 
                                                 "lh.GM.precuneus" = "Left Precuneus cortex", 
                                                 "lh.GM.rostralanteriorcingulate" = "Left Rostral anterior cingulate cortex", 
                                                 "lh.GM.rostralmiddlefrontal" = "Left Rostral middle frontal gyrus", 
                                                 "lh.GM.superiorfrontal" = "Left Superior frontal gyrus", 
                                                 "lh.GM.superiorparietal" = "Left Superior parietal cortex", 
                                                 "lh.GM.superiortemporal" = "Left Superior temporal gyrus", 
                                                 "lh.GM.supramarginal" = "Left Supramarginal gyrus", 
                                                 "lh.GM.frontalpole" = "Left Frontal pole", 
                                                 "lh.GM.temporalpole" = "Left Temporal pole", 
                                                 "lh.GM.transversetemporal" = "Left Transverse temporal cortex", 
                                                 "lh.GM.insula" = "Left Insula"))

#expand cols (by predictor)
tails_results_html <- results_html2 %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  group_by(predictor, dependent, Estimate_Type) %>%
  mutate(dup_id = row_number()) %>%
  ungroup()%>%
  pivot_wider(
    names_from = c(dependent, Estimate_Type),
    values_from = Estimate,
    names_sep = "_",
    id_cols = c(predictor, dup_id)
  ) %>%
  select(-dup_id)

#create a variable that groups by predictor (ie: model) 
imaging_predictors <- tails_results_html$predictor[seq(1, length(tails_results_html$predictor), by = 9)]
tails_results_html$predictor_group <- rep(imaging_predictors, each = 9)

#add hemisphere variable 
tails_results_html <- tails_results_html %>%
  mutate(hemisphere = case_when(startsWith(as.character(predictor_group), "Left") ~ "Left", 
                                startsWith(as.character(predictor_group), "Right") ~ "Right"))%>%
  mutate(predictor = case_when(startsWith(as.character(predictor), "Left") ~ "Regional Predictor", 
                               startsWith(as.character(predictor), "Right") ~ "Regional Predictor", 
                               TRUE ~ predictor))

#Create a formatted regression table 
tails_regression_table <- tails_results_html %>%
  mutate(predictor = recode(predictor,"age" = "Age", "sex" = "Sex", "site" = "Site ID", "puberty" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))%>%
  gt(groupname_col = "predictor_group", rowname_col = "predictor") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using regional cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    bw_formatted_raw_est = "Raw", bw_formatted_std_est = "Standardized",
    ga_group_formatted_raw_est = "Raw", ga_group_formatted_std_est = "Standardized",
    bmi_formatted_raw_est = "Raw", bmi_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Birthweight",
    columns = c(bw_formatted_raw_est, bw_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Gestational Age",
    columns = c(ga_group_formatted_raw_est, ga_group_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Body Mass Index",
    columns = c(bmi_formatted_raw_est, bmi_formatted_std_est)
  ) %>%
  row_group_order(groups = unique(tails_results_html$predictor_group)) # Order models if necessary
```

Save the table as an HTML file
```{r}
tails_regression_table %>%
  gtsave("bio_regional_tails_table.html")
```

Format dimensional data: 
```{r}
#add significance
results_html3<- results3 %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

results_html3$formatted_raw_est <- paste0(round(results_html3$est,2), ", (", round(results_html3$se,2), ")")
results_html3$formatted_std_est <- paste0(round(results_html3$beta,2), results_html3$significance)

results_html3 <- results_html3 %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)

#rename v's
results_html3$dependent<- (factor(results_html3$dependent, levels = c("bmi", "ga_group", "bw")))

results_html3$predictor<-gsub('Transformed.q.wre','',results_html3$predictor)

results_html3$predictor<- revalue(results_html3$predictor, c("rh.GM.bankssts" = "Right Banks of the superior temporal sulcus", 
                                                 "rh.GM.caudalanteriorcingulate" = "Right Caudal anterior cingulate cortex", 
                                                 "rh.GM.caudalmiddlefrontal" = "Right Caudal middle frontal gyrus", 
                                                 "rh.GM.cuneus" = "Right Cuneus cortex", 
                                                 "rh.GM.entorhinal" = "Right Entorhinal cortex", 
                                                 "rh.GM.fusiform" = "Right Fusiform gyrus", 
                                                 "rh.GM.inferiorparietal" = "Right Inferior parietal cortex", 
                                                 "rh.GM.inferiortemporal" = "Right Inferior temporal gyrus",
                                                 "rh.GM.isthmuscingulate" = "Right Isthmus Anterior Cingulate cortex", 
                                                 "rh.GM.lateraloccipital" = "Right Lateral occipital cortex", 
                                                 "rh.GM.lateralorbitofrontal" = "Right Lateral Orbitofrontal cortex", 
                                                 "rh.GM.lingual" = "Right Lingual gyrus", 
                                                 "rh.GM.medialorbitofrontal" = "Right Medial Orbitofrontal cortex", 
                                                 "rh.GM.middletemporal" = "Right Middle temporal gyrus", 
                                                 "rh.GM.parahippocampal" = "Right Parahippocampal gyrus", 
                                                 "rh.GM.paracentral" = "Right Paracentral lobule", 
                                                 "rh.GM.parsopercularis" = "Right Pars opercularis", 
                                                 "rh.GM.parsorbitalis" = "Right Pars orbitalis", 
                                                 "rh.GM.parstriangularis" = "Right Pars triangularis", 
                                                 "rh.GM.pericalcarine" = "Right Pericalcarine cortex", 
                                                 "rh.GM.postcentral" = "Right Postcentral gyrus", 
                                                 "rh.GM.posteriorcingulate" = "Right Posterior anterior cingulate cortex", 
                                                 "rh.GM.precentral" = "Right Precentral gyrus", 
                                                 "rh.GM.precuneus" = "Right Precuneus cortex", 
                                                 "rh.GM.rostralanteriorcingulate" = "Right Rostral anterior cingulate cortex", 
                                                 "rh.GM.rostralmiddlefrontal" = "Right Rostral middle frontal gyrus", 
                                                 "rh.GM.superiorfrontal" = "Right Superior frontal gyrus", 
                                                 "rh.GM.superiorparietal" = "Right Superior parietal cortex", 
                                                 "rh.GM.superiortemporal" = "Right Superior temporal gyrus", 
                                                 "rh.GM.supramarginal" = "Right Supramarginal gyrus", 
                                                 "rh.GM.frontalpole" = "Right Frontal pole", 
                                                 "rh.GM.temporalpole" = "Right Temporal pole", 
                                                 "rh.GM.transversetemporal" = "Right Transverse temporal cortex", 
                                                 "rh.GM.insula" = "Right Insula", 
                                                 "lh.GM.bankssts" = "Left Banks of the superior temporal sulcus", 
                                                 "lh.GM.caudalanteriorcingulate" = "Left Caudal anterior cingulate cortex", 
                                                 "lh.GM.caudalmiddlefrontal" = "Left Caudal middle frontal gyrus", 
                                                 "lh.GM.cuneus" = "Left Cuneus cortex", 
                                                 "lh.GM.entorhinal" = "Left Entorhinal cortex", 
                                                 "lh.GM.fusiform" = "Left Fusiform gyrus", 
                                                 "lh.GM.inferiorparietal" = "Left Inferior parietal cortex", 
                                                 "lh.GM.inferiortemporal" = "Left Inferior temporal gyrus",
                                                 "lh.GM.isthmuscingulate" = "Left Isthmus Anterior Cingulate cortex", 
                                                 "lh.GM.lateraloccipital" = "Left Lateral occipital cortex", 
                                                 "lh.GM.lateralorbitofrontal" = "Left Lateral Orbitofrontal cortex", 
                                                 "lh.GM.lingual" = "Left Lingual gyrus", 
                                                 "lh.GM.medialorbitofrontal" = "Left Medial Orbitofrontal cortex", 
                                                 "lh.GM.middletemporal" = "Left Middle temporal gyrus", 
                                                 "lh.GM.parahippocampal" = "Left Parahippocampal gyrus", 
                                                 "lh.GM.paracentral" = "Left Paracentral lobule", 
                                                 "lh.GM.parsopercularis" = "Left Pars opercularis", 
                                                 "lh.GM.parsorbitalis" = "Left Pars orbitalis", 
                                                 "lh.GM.parstriangularis" = "Left Pars triangularis", 
                                                 "lh.GM.pericalcarine" = "Left Pericalcarine cortex", 
                                                 "lh.GM.postcentral" = "Left Postcentral gyrus", 
                                                 "lh.GM.posteriorcingulate" = "Left Posterior anterior cingulate cortex", 
                                                 "lh.GM.precentral" = "Left Precentral gyrus", 
                                                 "lh.GM.precuneus" = "Left Precuneus cortex", 
                                                 "lh.GM.rostralanteriorcingulate" = "Left Rostral anterior cingulate cortex", 
                                                 "lh.GM.rostralmiddlefrontal" = "Left Rostral middle frontal gyrus", 
                                                 "lh.GM.superiorfrontal" = "Left Superior frontal gyrus", 
                                                 "lh.GM.superiorparietal" = "Left Superior parietal cortex", 
                                                 "lh.GM.superiortemporal" = "Left Superior temporal gyrus", 
                                                 "lh.GM.supramarginal" = "Left Supramarginal gyrus", 
                                                 "lh.GM.frontalpole" = "Left Frontal pole", 
                                                 "lh.GM.temporalpole" = "Left Temporal pole", 
                                                 "lh.GM.transversetemporal" = "Left Transverse temporal cortex", 
                                                 "lh.GM.insula" = "Left Insula"))

#expand cols
dim_results_html <- results_html3 %>%
  select(dependent, predictor, formatted_raw_est, formatted_std_est)%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  group_by(predictor, dependent, Estimate_Type) %>%
  mutate(dup_id = row_number()) %>%
  ungroup()%>%
  pivot_wider(
    names_from = c(dependent, Estimate_Type),
    values_from = Estimate,
    names_sep = "_",
    id_cols = c(predictor, dup_id)
  ) %>%
  select(-dup_id)

#create a variable that groups by predictor (ie: model) 
imaging_predictors <- dim_results_html$predictor[seq(1, length(dim_results_html$predictor), by = 9)]
dim_results_html$predictor_group <- rep(imaging_predictors, each = 9)

#add hemisphere variable 
dim_results_html <- dim_results_html %>%
  mutate(hemisphere = case_when(startsWith(as.character(predictor_group), "Left") ~ "Left", 
                                startsWith(as.character(predictor_group), "Right") ~ "Right"))%>%
  mutate(predictor = case_when(startsWith(as.character(predictor), "Left") ~ "Regional Predictor", 
                               startsWith(as.character(predictor), "Right") ~ "Regional Predictor", 
                               TRUE ~ predictor))

#Create a formatted regression table 
dim_regression_table <- dim_results_html %>%
  mutate(predictor = recode(predictor,"age" = "Age", "sex" = "Sex", "site" = "Site ID", "puberty" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))%>%
  gt(groupname_col = "predictor_group", rowname_col = "predictor") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using regional cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    bw_formatted_raw_est = "Raw", bw_formatted_std_est = "Standardized",
    ga_group_formatted_raw_est = "Raw", ga_group_formatted_std_est = "Standardized",
    bmi_formatted_raw_est = "Raw", bmi_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Birthweight",
    columns = c(bw_formatted_raw_est, bw_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Gestational Age",
    columns = c(ga_group_formatted_raw_est, ga_group_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Body Mass Index",
    columns = c(bmi_formatted_raw_est, bmi_formatted_std_est)
  ) %>%
  row_group_order(groups = unique(dim_results_html$predictor_group)) # Order models if necessary

```

Save the table as an HTML file
```{r}
dim_regression_table %>%
  gtsave("bio_regional_dim_table.html")
```

-----------------------------------
Make Heatmap Figures
-----------------------------------

Split matched results by hemisphere so figure is more interpretable: 
```{r}
results_rh<- results %>%
  filter(str_starts(predictor, "rh."))%>% 
  mutate(hemisphere="Right Hemisphere")
results_rh$predictor<-gsub('Transformed.q.wre','',results_rh$predictor)
results_rh$predictor<-gsub('rh.GM.','',results_rh$predictor)

results_lh<- results %>% 
  filter(str_starts(predictor, "lh."))%>%
  mutate(hemisphere="Left Hemisphere")
results_lh$predictor<-gsub('Transformed.q.wre','',results_lh$predictor)
results_lh$predictor<-gsub('lh.GM.','',results_lh$predictor)
```

Reorder and rename as needed
```{r}
library(plyr)
results<- rbind(results_rh, results_lh)
results$dependent<- (factor(results$dependent, levels = c("bmi", "ga_group", "bw")))

results$predictor<- revalue(results$predictor, c("bankssts" = "Banks of the superior temporal sulcus", 
                                                 "caudalanteriorcingulate" = "Caudal anterior cingulate cortex", 
                                                 "caudalmiddlefrontal" = "Caudal middle frontal gyrus", 
                                                 "cuneus" = "Cuneus cortex", 
                                                 "entorhinal" = "Entorhinal cortex", 
                                                 "fusiform" = "Fusiform gyrus", 
                                                 "inferiorparietal" = "Inferior parietal cortex", 
                                                 "inferiortemporal" = "Inferior temporal gyrus",
                                                 "isthmuscingulate" = "Isthmus Anterior Cingulate cortex", 
                                                 "lateraloccipital" = "Lateral occipital cortex", 
                                                 "lateralorbitofrontal" = "Lateral Orbitofrontal cortex", 
                                                 "lingual" = "Lingual gyrus", 
                                                 "medialorbitofrontal" = "Medial Orbitofrontal cortex", 
                                                 "middletemporal" = "Middle temporal gyrus", 
                                                 "parahippocampal" = "Parahippocampal gyrus", 
                                                 "paracentral" = "Paracentral lobule", 
                                                 "parsopercularis" = "Pars opercularis", 
                                                 "parsorbitalis" = "Pars orbitalis", 
                                                 "parstriangularis" = "Pars triangularis", 
                                                 "pericalcarine" = "Pericalcarine cortex", 
                                                 "postcentral" = "Postcentral gyrus", 
                                                 "posteriorcingulate" = "Posterior anterior cingulate cortex", 
                                                 "precentral" = "Precentral gyrus", 
                                                 "precuneus" = "Precuneus cortex", 
                                                 "rostralanteriorcingulate" = "Rostral anterior cingulate cortex", 
                                                 "rostralmiddlefrontal" = "Rostral middle frontal gyrus", 
                                                 "superiorfrontal" = "Superior frontal gyrus", 
                                                 "superiorparietal" = "Superior parietal cortex", 
                                                 "superiortemporal" = "Superior temporal gyrus", 
                                                 "supramarginal" = "Supramarginal gyrus", 
                                                 "frontalpole" = "Frontal pole", 
                                                 "temporalpole" = "Temporal pole", 
                                                 "transversetemporal" = "Transverse temporal cortex", 
                                                 "insula" = "Insula"))
                                            
```

```{r}
p_both_h<- ggplot(results, aes(y = dependent, x = predictor, fill = beta)) +
  geom_tile(color = ifelse(results$ps_fdr < 0.05, "black", "grey"), 
            lwd = ifelse(results$ps_fdr < 0.05, 0.5, 0), 
            linetype = 1) + 
    scale_fill_gradientn(colors = custom_colors(5), limits = c(-0.37, 0.37))+
  scale_y_discrete(labels=c("BMI", "Gestational Age", "Birth Weight"))+
  coord_flip() +
  theme_minimal() +
  facet_grid(. ~ hemisphere,as.table = TRUE) +
  labs(x = "", y = "", fill = "Beta Value") +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust=1, hjust=1, size=12), 
        axis.text.y = element_text(size=12), 
        strip.text = element_text(size = 13))
p_both_h
ggsave(file="regional_bio_matched.svg", plot=p_both_h, width=10, height=8)
```
Now, in unmatched data 



Split by hemisphere so figure is more interpretable: 
```{r}
results_rh2<- results2 %>%
  filter(str_starts(predictor, "rh."))%>%
  mutate(hemisphere="Right Hemisphere")
results_rh2$predictor<-gsub('Transformed.q.wre','',results_rh2$predictor)
results_rh2$predictor<-gsub('rh.GM.','',results_rh2$predictor)

results_lh2<- results2 %>% 
  filter(str_starts(predictor, "lh."))%>%
  mutate(hemisphere="Left Hemisphere")
results_lh2$predictor<-gsub('Transformed.q.wre','',results_lh2$predictor)
results_lh2$predictor<-gsub('lh.GM.','',results_lh2$predictor)

results2<- rbind(results_rh2, results_lh2)
```

Reorder and rename as needed
```{r}
results2$dependent<- (factor(results2$dependent, levels = c("bmi", "ga_group", "bw")))

results2$predictor<- revalue(results2$predictor, c("bankssts" = "Banks of the superior temporal sulcus", 
                                                 "caudalanteriorcingulate" = "Caudal anterior cingulate cortex", 
                                                 "caudalmiddlefrontal" = "Caudal middle frontal gyrus", 
                                                 "cuneus" = "Cuneus cortex", 
                                                 "entorhinal" = "Entorhinal cortex", 
                                                 "fusiform" = "Fusiform gyrus", 
                                                 "inferiorparietal" = "Inferior parietal cortex", 
                                                 "inferiortemporal" = "Inferior temporal gyrus",
                                                 "isthmuscingulate" = "Isthmus Anterior Cingulate cortex", 
                                                 "lateraloccipital" = "Lateral occipital cortex", 
                                                 "lateralorbitofrontal" = "Lateral Orbitofrontal cortex", 
                                                 "lingual" = "Lingual gyrus", 
                                                 "medialorbitofrontal" = "Medial Orbitofrontal cortex", 
                                                 "middletemporal" = "Middle temporal gyrus", 
                                                 "parahippocampal" = "Parahippocampal gyrus", 
                                                 "paracentral" = "Paracentral lobule", 
                                                 "parsopercularis" = "Pars opercularis", 
                                                 "parsorbitalis" = "Pars orbitalis", 
                                                 "parstriangularis" = "Pars triangularis", 
                                                 "pericalcarine" = "Pericalcarine cortex", 
                                                 "postcentral" = "Postcentral gyrus", 
                                                 "posteriorcingulate" = "Posterior anterior cingulate cortex", 
                                                 "precentral" = "Precentral gyrus", 
                                                 "precuneus" = "Precuneus cortex", 
                                                 "rostralanteriorcingulate" = "Rostral anterior cingulate cortex", 
                                                 "rostralmiddlefrontal" = "Rostral middle frontal gyrus", 
                                                 "superiorfrontal" = "Superior frontal gyrus", 
                                                 "superiorparietal" = "Superior parietal cortex", 
                                                 "superiortemporal" = "Superior temporal gyrus", 
                                                 "supramarginal" = "Supramarginal gyrus", 
                                                 "frontalpole" = "Frontal pole", 
                                                 "temporalpole" = "Temporal pole", 
                                                 "transversetemporal" = "Transverse temporal cortex", 
                                                 "insula" = "Insula"))
                                            
```

```{r}
p_both_h2<- ggplot(results2, aes(y = dependent, x = predictor, fill = beta)) +
  geom_tile(color = ifelse(results2$ps_fdr < 0.05, "black", "grey"), 
            lwd = ifelse(results2$ps_fdr < 0.05, 0.5, 0), 
            linetype = 1) + 
  scale_fill_gradientn(colors = custom_colors(5), limits = c(-0.37, 0.37))+
  scale_y_discrete(labels=c("BMI", "Gestational Age", "Birth Weight"))+
  coord_flip() +
  theme_minimal() +
  facet_grid(. ~ hemisphere,as.table = TRUE) +
  labs(x = "", y = "", fill = "Beta Value") +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust=1, hjust=1, size=12), 
        axis.text.y = element_text(size=12), 
        strip.text = element_text(size = 13))
p_both_h2

ggsave(file="regional_bio_tails.svg", plot=p_both_h2, width=10, height=8)

```

Now, in dimensional data 

Split by hemisphere so figure is more interpretable: 
```{r}
results_rh3<- results3 %>%
  filter(str_starts(predictor, "rh."))%>%
  mutate(hemisphere="Right Hemisphere")
results_rh3$predictor<-gsub('Transformed.q.wre','',results_rh3$predictor)
results_rh3$predictor<-gsub('rh.GM.','',results_rh3$predictor)

results_lh3<- results3 %>% 
  filter(str_starts(predictor, "lh."))%>%
  mutate(hemisphere="Left Hemisphere")
results_lh3$predictor<-gsub('Transformed.q.wre','',results_lh3$predictor)
results_lh3$predictor<-gsub('lh.GM.','',results_lh3$predictor)

results3<- rbind(results_rh3, results_lh3)
```

Reorder and rename as needed
```{r}
results3$dependent<- (factor(results3$dependent, levels = c("bmi", "ga_group", "bw")))

results3$predictor<- revalue(results3$predictor, c("bankssts" = "Banks of the superior temporal sulcus", 
                                                 "caudalanteriorcingulate" = "Caudal anterior cingulate cortex", 
                                                 "caudalmiddlefrontal" = "Caudal middle frontal gyrus", 
                                                 "cuneus" = "Cuneus cortex", 
                                                 "entorhinal" = "Entorhinal cortex", 
                                                 "fusiform" = "Fusiform gyrus", 
                                                 "inferiorparietal" = "Inferior parietal cortex", 
                                                 "inferiortemporal" = "Inferior temporal gyrus",
                                                 "isthmuscingulate" = "Isthmus Anterior Cingulate cortex", 
                                                 "lateraloccipital" = "Lateral occipital cortex", 
                                                 "lateralorbitofrontal" = "Lateral Orbitofrontal cortex", 
                                                 "lingual" = "Lingual gyrus", 
                                                 "medialorbitofrontal" = "Medial Orbitofrontal cortex", 
                                                 "middletemporal" = "Middle temporal gyrus", 
                                                 "parahippocampal" = "Parahippocampal gyrus", 
                                                 "paracentral" = "Paracentral lobule", 
                                                 "parsopercularis" = "Pars opercularis", 
                                                 "parsorbitalis" = "Pars orbitalis", 
                                                 "parstriangularis" = "Pars triangularis", 
                                                 "pericalcarine" = "Pericalcarine cortex", 
                                                 "postcentral" = "Postcentral gyrus", 
                                                 "posteriorcingulate" = "Posterior anterior cingulate cortex", 
                                                 "precentral" = "Precentral gyrus", 
                                                 "precuneus" = "Precuneus cortex", 
                                                 "rostralanteriorcingulate" = "Rostral anterior cingulate cortex", 
                                                 "rostralmiddlefrontal" = "Rostral middle frontal gyrus", 
                                                 "superiorfrontal" = "Superior frontal gyrus", 
                                                 "superiorparietal" = "Superior parietal cortex", 
                                                 "superiortemporal" = "Superior temporal gyrus", 
                                                 "supramarginal" = "Supramarginal gyrus", 
                                                 "frontalpole" = "Frontal pole", 
                                                 "temporalpole" = "Temporal pole", 
                                                 "transversetemporal" = "Transverse temporal cortex", 
                                                 "insula" = "Insula"))
                                            
```

```{r}
p_both_h3<- ggplot(results3, aes(y = dependent, x = predictor, fill = beta)) +
  geom_tile(color = ifelse(results3$ps_fdr < 0.05, "black", "grey"), 
            lwd = ifelse(results3$ps_fdr < 0.05, 0.5, 0), 
            linetype = 1) + 
  scale_fill_gradientn(colors = custom_colors(5), limits = c(-0.37, 0.37))+
    scale_y_discrete(labels=c("BMI", "Gestational Age", "Birth Weight"))+
  coord_flip() +
  theme_minimal() +
  facet_grid(. ~ hemisphere,as.table = TRUE) +
  labs(x = "", y = "", fill = "Beta Value") +
  theme_classic()+
  theme(axis.text.x = element_text(angle = 45, vjust=1, hjust=1, size=12), 
        axis.text.y = element_text(size=12), 
        strip.text = element_text(size = 13))
p_both_h3
ggsave(file="regional_bio_dimensional.svg", plot=p_both_h3, width=10, height=8)
```

Add in one figure 
```{r}
bio_fig<- ggarrange(p_both_h, p_both_h2,p_both_h3,  nrow=3, ncol=1, labels=c("Dimensional", "Tail-Sampled", "Propensity Matched"),
                        common.legend = T, legend="right")
bio_fig
```

Now put it on brains !
First, load the brain package and the atlas names 
```{r}
library(ggseg)
setwd('~/Downloads')
atlas_regions<- read.csv('dk_ggseg.csv')
atlas_regions<- c(atlas_regions$x, atlas_regions$x)
```

We want to project the number of significant relationships across tasks are present across each region. 

Create a variable per each results data set that sums how many significant relationships there are per predictor(start with matched results)
```{r}
results_wide_left<- results%>%
  filter(hemisphere=="Left Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Left Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide_right<- results%>%
  filter(hemisphere=="Right Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Right Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide<- rbind(results_wide_left, results_wide_right)
results_wide$region<- atlas_regions
```

And project this to a brain
```{r}
match_brain<- results_wide%>%
  ggplot()+
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = num_sig)) +
  scale_fill_gradient2(
    low = "white", 
    mid = "yellow", 
    high = "red", 
    midpoint = 1.5, 
    limits = c(0, 3),  # Ensure the scale includes zero
  ) + theme_classic() + labs(fill="Number of Significant Predictors")
match_brain

ggsave(file="brain_bio_matched.svg", plot=match_brain, width=10, height=8)
``` 

Repeat with tail-sampled results 
```{r}
results_wide_left2<- results2%>%
  filter(hemisphere=="Left Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Left Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide_right2<- results2%>%
  filter(hemisphere=="Right Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  dplyr::mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Right Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide2<- rbind(results_wide_left2, results_wide_right2)
results_wide2$region<- atlas_regions
```

And project this to a brain
```{r}
tail_brain<-results_wide2%>%
  ggplot()+
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = num_sig)) +
  scale_fill_gradient2(
    low = "white", 
    mid = "yellow", 
    high = "red", 
    midpoint = 1.5, 
    limits = c(0, 3),  # Ensure the scale includes zero
  ) + theme_classic() + labs(fill="Number of Significant Predictors")
tail_brain
ggsave(file="brain_bio_tails.svg", plot=tail_brain, width=10, height=8)
```

And again for dimensional results 

```{r}
results_wide_left3<- results3%>%
  filter(hemisphere=="Left Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Left Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide_right3<- results3%>%
  filter(hemisphere=="Right Hemisphere")%>%
  select(predictor, dependent, ps_fdr)%>%
  pivot_wider(names_from = dependent, values_from = ps_fdr)%>%
  mutate(num_sig = rowSums(across(where(is.numeric), ~ . < 0.05)))%>%
  mutate(hemisphere="Right Hemisphere")%>%
  select(predictor, num_sig, hemisphere)

results_wide3<- rbind(results_wide_left3, results_wide_right3)
results_wide3$region<- atlas_regions
```

And project this to a brain
```{r}
dim_brain<-results_wide3%>%
  ggplot()+
  geom_brain(atlas = dk, 
             position = position_brain(hemi ~ side),
             aes(fill = num_sig)) +
  scale_fill_gradient2(
    low = "white", 
    mid = "yellow", 
    high = "red", 
    midpoint = 1.5, 
    limits = c(0, 3),  # Ensure the scale includes zero
  ) + theme_classic() + labs(fill="Number of Significant Predictors")
dim_brain
ggsave(file="brain_bio_dimensional.svg", plot=dim_brain, width=10, height=8)
```

Arrange 
```{r}
brain_dim_fig<- ggarrange(p_both_h3,dim_brain,  nrow=2, ncol=1, labels=c("A", "Dimensional"))
brain_dim_fig

brain_tail_fig<- ggarrange(p_both_h2,tail_brain, nrow=2, ncol=1, labels=c("B", "Tail-Sampled"))
brain_tail_fig

brain_match_fig<- ggarrange( p_both_h,match_brain, nrow=2, ncol=1, labels=c("C", "Propensity Matched"))
brain_match_fig
```

