---
title: "Topography Matching Notebook"
output:
  html_document:
    df_print: paged
---

This R Notebook documents the steps taken to organize the data used for EDEN Lab's imaging propensity matching projects for the ABCD Dataset.

First, install necessary packages.

```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(tidyverse)
library(rstatix)
library(ggpubr)
```

Specify that select function should be pulled from dplyr
```{r}
select <- dplyr::select
`%ni%` = Negate(`%in%`)
```

Next, log into PennBox, and set working directory the project directory.
```{r}
box_auth()

box_setwd('203279384208')
```

Read in covariate data, including T1 demos, family/site id's (filter for T1, select relevant v's). 
```{r}
#read in demos
demos<-box_read('1277081419111', fread=TRUE)
demos_trimmed<- as_tibble(demos)%>%
  select(src_subject_id, demo_brthdat_v2, eventname, demo_sex_v2, demo_prnt_ed_v2, demo_comb_income_v2,
         demo_ethn_v2)%>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA" 

#read in id's 
ids<-box_read('1277070740402', fread=T)
ids$site_id_l<-gsub('site','',ids$site_id_l)
ids<-as_tibble(ids)%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  select(src_subject_id, site_id_l, rel_family_id)
```

Read in 7-category race that I coded earlier. 
```{r}
race<-box_read('1422910727882', fread=TRUE)
race<- as_tibble(race)%>%
  select(src_subject_id, race3)
```

read in puberty data (youth report) and collapse into one measure
```{r}
youth_pub<-box_read('1277086204139', fread=TRUE)
youth_pub<-as_tibble(youth_pub)%>%
  filter(eventname=="baseline_year_1_arm_1")%>%
  select(src_subject_id, pds_sex_y, pds_y_ss_male_cat_2, pds_y_ss_female_category_2)%>%
  mutate(across(everything(), ~ifelse(.=="777", NA, as.character(.))))%>% #recode "unknown" cells as "NA" 
  mutate(across(everything(), ~ifelse(.=="999", NA, as.character(.))))#recode "refused" cells as "NA" 
  
yf_pub1<-filter(youth_pub, pds_sex_y == 2)%>%
  select(src_subject_id, pds_y_ss_female_category_2)%>%
  rename(pds_y_ss = pds_y_ss_female_category_2)
ym_pub1<-filter(youth_pub, pds_sex_y == 1)%>%
  select(src_subject_id, pds_y_ss_male_cat_2)%>%
  rename(pds_y_ss = pds_y_ss_male_cat_2)

ypub1<-rbind(yf_pub1, ym_pub1)
```

Now read in imaging inclusion data to match on:
```{r}
imaging_include<-box_read('1277078814392', fread=TRUE)
imaging_include<-as_tibble(imaging_include)%>%
  filter(eventname=='baseline_year_1_arm_1')%>%
  select(src_subject_id, imgincl_t1w_include, imgincl_t2w_include)
```

Read in Structural Data/ motion measure, and add to data

```{r}
centiles<- box_read('1267779812594', fread=T)
centiles$participant<-gsub('sub-NDARINV','NDAR_INV',centiles$participant)

centiles<- rename(centiles, src_subject_id = participant)%>%
  select(-sex, -site)

euler<-box_read('1314622137417', fread=TRUE)
euler$id<-gsub('sub-NDARINV','NDAR_INV',euler$id)
euler<- rename(euler, src_subject_id = id)
```
Merge with matching data, and select relevant columns

```{r}
matching_data<- merge(ids, centiles, all.x=T)
matching_data<- merge(matching_data, demos_trimmed)
matching_data<- merge(matching_data, race, all=T)
matching_data<- merge(matching_data, ypub1, all=T)
matching_data<- merge(matching_data, imaging_include, all.x=T)
matching_data<- merge(matching_data, euler, all.x=T)
```

write out this data set 
```{r}
#box_write(matching_data, file_name='matching_data_n11868_04.08.24.csv', dir_id ='203279384208')
```

```{r}
data_trim<-matching_data%>%
  filter(imgincl_t1w_include == 1)%>%
  filter(imgincl_t2w_include == 1)%>%
  dplyr::select(src_subject_id, demo_brthdat_v2, sex_recode,
         site_id,pds_y_ss,demo_ethn_v2_recode, race3, Family,
         demo_prnt_ed_v2, demo_comb_income_v2)%>%
  mutate_at(c('demo_brthdat_v2','sex_recode', 'site_id',
              'pds_y_ss','demo_ethn_v2_recode', 'race3', 'Family',
              'demo_prnt_ed_v2', 'demo_comb_income_v2'),as.numeric)%>%
  mutate(age_by_sex=(sex_recode*demo_brthdat_v2))%>%
  drop_na() 
```

Rename variables for clarity.

```{r}
cols<-colnames(data_trim)
cols
```

```{r}
cols2<- c('subjectkey', 'age', 'sex', 'site_id', 'puberty_stage', 'ethnicity', 'race_3', 'family', 'parent_education', 'combined_income', 'age_by_sex')
data_clean<-data_trim %>%
  rename_at(all_of(cols), ~cols2)
```

Read in Structural Data and wrangle

```{r}
centiles<- box_read('1267779812594', fread=T)
centiles$participant<-gsub('sub-NDARINV','NDAR_INV',centiles$participant)

centiles<- rename(centiles, subjectkey = participant)

euler<-box_read('1314622137417', fread=TRUE)
euler$id<-gsub('sub-NDARINV','NDAR_INV',euler$id)
euler<- rename(euler, subjectkey = id)
```

merge together
```{r}
all_data<- centiles%>%
  select(-c(site, sex))%>%
  merge(data_clean, by='subjectkey')

all_data<-merge(all_data, euler)
```

randomly select one sibling per family 
```{r}
set.seed(12345) 

all_data <-all_data %>% group_by(family) %>% slice_sample(n = 1) %>%  ungroup() 
```

Check distributions and save means and mads for indexing

```{r}
all_data%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  hist.data.frame()

all_data%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  psych::describe()

mads<-all_data%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  psych::describe()%>%
  as_tibble()%>%
  select(mean, median, mad)%>%
  as.data.frame()

rownames(mads)<-c('GMV','WMV','sGMV','Ventricles')
```

Save unmatched data for comparison. First, keep dimensional network sizes. 
```{r}
#box_write(all_data, file_name='unmatched_dimensional_data.02.05.24.csv', dir_id='218960591983')
```


Calculate high/low values and create group variable for each network (high= 1, treatment; low= 0, control), using p's one MAD above/below median (look in the tails). 

```{r}
high1<- filter(all_data, GMV>(mads[1,2]+mads[1,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low1<- filter(all_data, GMV<(mads[1,2]-mads[1,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
GMV<-rbind(high1, low1)

high2<- filter(all_data, WMV>(mads[2,2]+mads[2,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low2<- filter(all_data, WMV<(mads[2,2]-mads[2,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
WMV<-rbind(high2, low2)

high3<- filter(all_data, sGMV>(mads[3,2]+mads[3,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low3<- filter(all_data, sGMV<(mads[3,2]-mads[3,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
sGMV<-rbind(high3, low3)

high4<- filter(all_data, Ventricles>(mads[4,2]+mads[4,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low4<- filter(all_data, Ventricles<(mads[4,2]-mads[4,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
Vent<-rbind(high4, low4)
```

merge each network group with clean data for matching

```{r}
GMV<-merge(GMV, all_data)
WMV<-merge(WMV, all_data) 
sGMV<-merge(sGMV, all_data)
Vent<-merge(Vent, all_data)
```

write out median +/- 1 MAD split data. 

```{r}
#box_write(GMV, file_name='MAD_split_gmv_data_02.05.24.csv', dir_id='218960591983')
#box_write(WMV, file_name='MAD_split_wmv_data_02.05.24.csv', dir_id='218960591983')
#box_write(sGMV, file_name='MAD_split_sgmv_data_02.05.24.csv', dir_id='218960591983')
#box_write(Vent, file_name='MAD_split_vent_data_02.05.24.csv', dir_id='218960591983')
```

```{r}
new.names <- c(age = "Age (Years)",
               sex_2 = "Sex",
               age_by_sex = "Age*Sex",
               site_id = "Site ID",
               race_3 = "Race",
               puberty_stage = "Puberty Stage",
               ethnicity = "Ethnicity",
               parent_education = "Parent Education",
               combined_income = "Household Income",
               euler = "Motion"
)

```
match each measure:

GMV:

```{r}
match_GMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 + 
                       parent_education + combined_income + euler,
                     data = GMV, caliper=0.1, method = "nearest", distance = "glm")

summary(match_GMV) 
love.plot(match_GMV,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)

match_GMV_data <- match.data(match_GMV)
#box_write(match_GMV_data, file_name='match_GMV_data_treat_high_02.05.24.csv', dir_id='218960591983')
```

compare means


WMV: 

```{r}
match_WMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                       parent_education + combined_income + euler, 
                     data = WMV, caliper=0.1, method = "nearest", distance = "glm")

summary(match_WMV)
love.plot(match_WMV,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)

match_WMV_data <- match.data(match_WMV)
#box_write(match_WMV_data, file_name='match_WMV_data_treat_high_02.05.24.csv', dir_id='218960591983')
```



sGMV: 

```{r}
match_sGMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                        parent_education + combined_income+ euler, 
                     data = sGMV, caliper=0.1, method = "nearest", distance = "glm")

summary(match_sGMV)
love.plot(match_sGMV,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)


match_sGMV_data <- match.data(match_sGMV)
#box_write(match_sGMV_data, file_name='match_sGMV_data_treat_high_02.05.24.csv', dir_id='218960591983')
```

Vent: 

```{r}
match_vent <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                      parent_education + combined_income+ euler, 
                     data = Vent, caliper=0.05, method = "nearest", distance = "glm")

summary(match_vent)
love.plot(match_vent,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)

match_vent_data <- match.data(match_vent)
#box_write(match_vent_data, file_name='match_vent_data_treat_high_02.05.24.csv', dir_id='218960591983')
```

Redo based with re-assigned treatment and control groups (ie: low=1, high=0)

Calculate high/low values and create group variable for each network:

```{r}
high1<- filter(all_data, GMV>(mads[1,2]+mads[1,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low1<- filter(all_data, GMV<(mads[1,2]-mads[1,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
GMV_2<-rbind(high1, low1)

high2<- filter(all_data, WMV>(mads[2,2]+mads[2,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low2<- filter(all_data, WMV<(mads[2,2]-mads[2,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
WMV_2<-rbind(high2, low2)

high3<- filter(all_data, sGMV>(mads[3,2]+mads[3,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low3<- filter(all_data, sGMV<(mads[3,2]-mads[3,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
sGMV_2<-rbind(high3, low3)

high4<- filter(all_data, Ventricles>(mads[4,2]+mads[4,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low4<- filter(all_data, Ventricles<(mads[4,2]-mads[4,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
Vent_2<-rbind(high4, low4)
```

merge each network group with clean data for matching

```{r}
GMV_2<-merge(GMV_2, all_data)
WMV_2<-merge(WMV_2, all_data) 
sGMV_2<-merge(sGMV_2, all_data)
Vent_2<-merge(Vent_2, all_data)
```

and match each network

```{r}
match_GMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                         parent_education + combined_income + euler, 
                     data = GMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_GMV_2)
love.plot(match_GMV_2,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)

match_GMV_data_2 <- match.data(match_GMV_2)
#box_write(match_GMV_data_2, file_name='match_GMV_data_treat_low_02.05.24.csv', dir_id='218960591983')
```

```{r}
match_WMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                        parent_education + combined_income+ euler, 
                     data =  WMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_WMV_2)
love.plot(match_WMV_2,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)

match_WMV_data_2 <- match.data(match_WMV_2)
#box_write(match_WMV_data_2, file_name='match_WMV_data_treat_low_02.05.24.csv', dir_id='218960591983')
```

```{r}
match_sGMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                          parent_education + combined_income+ euler, 
                     data =  sGMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_sGMV_2)
love.plot(match_sGMV_2,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)


match_sGMV_data_2 <- match.data(match_sGMV_2)
#box_write(match_sGMV_data_2, file_name='match_sGMV_data_treat_low_02.05.24.csv', dir_id='218960591983')
```

```{r}
match_vent_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                          parent_education + combined_income+ euler, 
                     data =  Vent_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_vent_2)
love.plot(match_vent_2,  drop.distance=TRUE, binary = "std", thresholds = c(m = .1), colors = c("red", "blue"), var.names =new.names)


match_vent_data_2 <- match.data(match_vent_2)
#box_write(match_vent_data_2, file_name='match_vent_data_treat_low_02.05.24.csv', dir_id='218960591983')
```

Check overlap between samples for each measure on high/low (ie: are the target high participants the same as the people who were pulled to match the target low participants)

GMV (target=high)
```{r}
gmv_target_high<- filter(match_GMV_data, group==1)
gmv_match_high<- filter(match_GMV_data_2, group==0)

high_gmv_ids<-(intersect(gmv_target_high$subjectkey ,gmv_match_high$subjectkey))
high_gmv<-filter(match_GMV_data, subjectkey %in% high_gmv_ids)
```

GMV (target=low)
```{r}
gmv_target_low<- filter(match_GMV_data_2, group==1)
gmv_match_low<- filter(match_GMV_data, group==0)

low_gmv_ids<-(intersect(gmv_target_low$subjectkey ,gmv_match_low$subjectkey))
low_gmv<-filter(match_GMV_data, subjectkey %in% low_gmv_ids)
```

all gmv:
```{r}
match_gmv<- rbind(high_gmv, low_gmv)
#box_write(match_gmv, file_name='match_gmv_data_overlap_02.05.24.csv', dir_id='218960591983')
```

WMV (target=high)
```{r}
wmv_target_high<- filter(match_WMV_data, group==1)
wmv_match_high<- filter(match_WMV_data_2, group==0)

high_wmv_ids<-(intersect(wmv_target_high$subjectkey ,wmv_match_high$subjectkey))
high_wmv<-filter(match_WMV_data, subjectkey %in% high_wmv_ids)
```

WMV (target=low)
```{r}
wmv_target_low<- filter(match_WMV_data_2, group==1)
wmv_match_low<- filter(match_WMV_data, group==0)

low_wmv_ids<-(intersect(wmv_target_low$subjectkey ,wmv_match_low$subjectkey))
low_wmv<-filter(match_WMV_data, subjectkey %in% low_wmv_ids)
```

all wmv:
```{r}
match_wmv<- rbind(high_wmv, low_wmv)
#box_write(match_wmv, file_name='match_wmv_data_overlap_02.05.24.csv', dir_id='218960591983')
```

sGMV (target=high)
```{r}
sgmv_target_high<- filter(match_sGMV_data, group==1)
sgmv_match_high<- filter(match_sGMV_data_2, group==0)

high_sgmv_ids<-(intersect(sgmv_target_high$subjectkey ,sgmv_match_high$subjectkey))
high_sgmv<-filter(match_sGMV_data, subjectkey %in% high_sgmv_ids)
```

sGMV (target=low)
```{r}
sgmv_target_low<- filter(match_sGMV_data_2, group==1)
sgmv_match_low<- filter(match_sGMV_data, group==0)

low_sgmv_ids<-(intersect(sgmv_target_low$subjectkey ,sgmv_match_low$subjectkey))
low_sgmv<-filter(match_sGMV_data, subjectkey %in% low_sgmv_ids)
```

all sgmv:
```{r}
match_sgmv<- rbind(high_sgmv, low_sgmv)
#box_write(match_sgmv, file_name='match_sgmv_data_overlap_02.05.24.csv', dir_id='218960591983')
```

vent (target=high)
```{r}
vent_target_high<- filter(match_vent_data, group==1)
vent_match_high<- filter(match_vent_data_2, group==0)

high_vent_ids<-(intersect(vent_target_high$subjectkey ,vent_match_high$subjectkey))
high_vent<-filter(match_vent_data, subjectkey %in% high_vent_ids)
```

vent (target=low)
```{r}
vent_target_low<- filter(match_vent_data_2, group==1)
vent_match_low<- filter(match_vent_data, group==0)

low_vent_ids<-(intersect(vent_target_low$subjectkey ,vent_match_low$subjectkey))
low_vent<-filter(match_vent_data, subjectkey %in% low_vent_ids)
```

all vent:
```{r}
match_vent<- rbind(high_vent, low_vent)
#box_write(match_vent, file_name='match_vent_data_overlap_02.05.24.csv', dir_id='218960591983')
```
Graph distributions 

```{r}
hist(match_gmv$GMV)
g1<-ggplot(match_gmv, aes(x=GMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white") +
 geom_density(alpha=.2, fill="#FF6666") 

g2<-ggplot(GMV, aes(x=GMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

g3<-ggplot(centiles, aes(x=GMV))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

gplots<-ggarrange(g3,g2,g1, nrow=3, ncol=1)
gplots
```

```{r}
w1<-ggplot(match_wmv, aes(x=WMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

w2<-ggplot(WMV, aes(x=WMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

w3<-ggplot(centiles, aes(x=WMV))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

wplots<-ggarrange(w3,w2,w1, nrow=3, ncol=1)
wplots
```
```{r}
s1<-ggplot(match_sgmv, aes(x=sGMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

s2<-ggplot(sGMV, aes(x=sGMV)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

s3<-ggplot(centiles, aes(x=sGMV))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 


splots<-ggarrange(s3,s2,s1, nrow=3, ncol=1)
splots
```
```{r}
v1<-ggplot(match_vent, aes(x=Ventricles)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

v2<-ggplot(Vent, aes(x=Ventricles)) +geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

v3<-ggplot(centiles, aes(x=Ventricles))+geom_histogram(aes(y=..density..), colour="black", fill="white")+
 geom_density(alpha=.2, fill="#FF6666") 

vplots<-ggarrange(v3,v2,v1, nrow=3, ncol=1)
vplots
```

Check race breakdown for each sample
```{r}
ggplot(match_gmv, aes(x=race_3)) +geom_histogram()
ggplot(match_wmv, aes(x=race_3)) +geom_histogram()
ggplot(match_sgmv, aes(x=race_3)) +geom_histogram()
ggplot(match_vent, aes(x=race_3)) +geom_histogram()
```

Filter for white/black participants 
```{r}
prs_gmv<- filter(match_gmv, race_3%in%c(1,2)) #646
length(prs_gmv$subjectkey) 
length(match_gmv$subjectkey)
prs_wmv<- filter(match_wmv, race_3%in%c(1,2)) #845
length(prs_wmv$subjectkey)
length(match_wmv$subjectkey)
prs_sgmv<- filter(match_sgmv, race_3%in%c(1,2)) #756
length(prs_sgmv$subjectkey)
length(match_sgmv$subjectkey)
prs_vent<- filter(match_vent, race_3%in%c(1,2)) #472
length(prs_vent$subjectkey)
length(match_vent$subjectkey)
```
Check differences in demographics across target/matched groups per measure

high gmv (target=1, match=0)
```{r}
rbind(gmv_target_high, gmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low gmv (target=1, match=0)
```{r}
rbind(gmv_target_low, gmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high wmv (target=1, match=0)
```{r}
rbind(wmv_target_high, wmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low wmv (target=1, match=0)
```{r}
rbind(wmv_target_low, wmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high sgmv (target=1, match=0)
```{r}
rbind(sgmv_target_high, sgmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low sgmv (target=1, match=0)
```{r}
rbind(sgmv_target_low, sgmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high vent (target=1, match=0)
```{r}
rbind(vent_target_high, vent_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low vent (target=1, match=0)
```{r}
rbind(vent_target_low, vent_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```
