---
title: "Topography Matching Notebook Step 2"
output:
  html_document:
    df_print: paged
---

This R Notebook runs multivariate multiple regression to model the cumulative effects of network group on clinical, cognitive and exposome outcomes:

First, install necessary packages.

```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(lm.beta)
library(ggpubr)
library(bayesbio)
library(mde)
library(lavaan) 
library(knitr)
library(kableExtra)
library(broom)
library(multcomp)
library(Gmisc)
```

Specify that select function should be pulled from dplyr

```{r}
select <- dplyr::select
recode <- dplyr::recode

`%ni%` <- Negate(`%in%`)
```

Next, log into PennBox, and set working directory the ABCD directory.

```{r}
box_auth()

box_setwd('167848222541')
```

Load in matched network data, code new group variable:
```{r}
match_vent_data<-box_read('1438682877497', fread=TRUE)
match_vent_data<- match_vent_data %>%
  mutate(anova_group = case_when(group == 0 ~ 'match_low', 
                                 group == 1 ~ 'match_high'))%>%
  select(-group, -distance, -weights, -subclass)
match_sGMV_data<-box_read('1438681749218', fread=TRUE)
match_sGMV_data<- match_sGMV_data %>%
  mutate(anova_group = case_when(group == 0 ~ 'match_low', 
                                 group == 1 ~ 'match_high'))%>%
  select(-group, -distance, -weights, -subclass)
match_WMV_data<-box_read('1438687945370', fread=TRUE)
match_WMV_data<- match_WMV_data %>%
  mutate(anova_group = case_when(group == 0 ~ 'match_low', 
                                 group == 1 ~ 'match_high'))%>%
  select(-group, -distance, -weights, -subclass)
match_GMV_data<-box_read('1438677748369', fread=TRUE)
match_GMV_data<- match_GMV_data %>%
  mutate(anova_group = case_when(group == 0 ~ 'match_low', 
                                 group == 1 ~ 'match_high'))%>%
  select(-group, -distance, -weights, -subclass)
```

load in unmatched network data, code new group variable: 
```{r}
unmatched_GMV_data<-box_read('1442236849436', fread=TRUE)
unmatched_GMV_data<- unmatched_GMV_data%>%
  filter(subjectkey %ni% match_GMV_data$subjectkey)%>%
  mutate(anova_group = case_when(group == 0 ~ 'tails_low', 
                                 group == 1 ~ 'tails_high'))%>%
  select(-group)

unmatched_WMV_data<-box_read('1442223376606', fread=TRUE)
unmatched_WMV_data<- unmatched_WMV_data %>%
  filter(subjectkey %ni% match_WMV_data$subjectkey)%>%
  mutate(anova_group = case_when(group == 0 ~ 'tails_low', 
                                 group == 1 ~ 'tails_high'))%>%
  select(-group)
  
unmatched_sGMV_data<-box_read('1442239979732', fread=TRUE)
unmatched_sGMV_data<- unmatched_sGMV_data%>%
  filter(subjectkey %ni% match_sGMV_data$subjectkey)%>%
  mutate(anova_group = case_when(group == 0 ~ 'tails_low', 
                                 group == 1 ~ 'tails_high'))%>%
  select(-group)

unmatched_vent_data<-box_read('1442240154828', fread=TRUE)
unmatched_vent_data <- unmatched_vent_data%>%
  filter(subjectkey %ni% match_vent_data$subjectkey)%>%
  mutate(anova_group = case_when(group == 0 ~ 'tails_low', 
                                 group == 1 ~ 'tails_high'))%>%
  select(-group)
```

Load in dimensional network data, identify p's who are not in other samples (ie: matched, tails): 
```{r}
all_dimensional_data<-box_read('1442204075893', fread=TRUE)

avg_GMV_data<- filter(all_dimensional_data, subjectkey %ni% match_GMV_data$subjectkey)%>%
  filter(subjectkey %ni% unmatched_GMV_data$subjectkey)%>%
  mutate(anova_group = 'avg')

avg_WMV_data<- filter(all_dimensional_data, subjectkey %ni% match_WMV_data$subjectkey)%>%
  filter(subjectkey %ni% unmatched_WMV_data$subjectkey)%>%
  mutate(anova_group = 'avg')

avg_sGMV_data<- filter(all_dimensional_data, subjectkey %ni% match_sGMV_data$subjectkey)%>%
  filter(subjectkey %ni% unmatched_sGMV_data$subjectkey)%>%
  mutate(anova_group = 'avg')

avg_vent_data<- filter(all_dimensional_data, subjectkey %ni% match_vent_data$subjectkey)%>%
  filter(subjectkey %ni% unmatched_vent_data$subjectkey)%>%
  mutate(anova_group = 'avg')
```

Make datasets of each tissue type with new anova group variable, make it a factor, and make sure that all chi-square v's are factors. 
```{r}
all_GMV_data<- rbind(match_GMV_data, unmatched_GMV_data, avg_GMV_data)%>%
  mutate(anova_group = as.factor(anova_group))%>%
  mutate(sex = as.factor(sex))%>%
  mutate(race_3 = as.factor(race_3))%>%
  mutate(site_id = as.factor(site_id))%>%
  mutate(ethnicity = as.factor(ethnicity))

all_WMV_data<- rbind(match_WMV_data, unmatched_WMV_data, avg_WMV_data)%>%
  mutate(anova_group = as.factor(anova_group))%>%
  mutate(sex = as.factor(sex))%>%
  mutate(race_3 = as.factor(race_3))%>%
  mutate(site_id = as.factor(site_id))%>%
  mutate(ethnicity = as.factor(ethnicity))

all_sGMV_data<- rbind(match_sGMV_data, unmatched_sGMV_data, avg_sGMV_data)%>%
  mutate(anova_group = as.factor(anova_group))%>%
  mutate(sex = as.factor(sex))%>%
  mutate(race_3 = as.factor(race_3))%>%
  mutate(site_id = as.factor(site_id))%>%
  mutate(ethnicity = as.factor(ethnicity))

all_vent_data<- rbind(match_vent_data, unmatched_vent_data, avg_vent_data)%>%
  mutate(anova_group = as.factor(anova_group))%>%
  mutate(sex = as.factor(sex))%>%
  mutate(race_3 = as.factor(race_3))%>%
  mutate(site_id = as.factor(site_id))%>%
  mutate(ethnicity = as.factor(ethnicity))
```

Make Demo Tables
```{r}
GMV_table <- all_GMV_data %>%
  set_column_labels(age = "Age (Years)",
                    sex = "Sex",
                    puberty_stage = "Pubertal Stage", 
                    ethnicity = 'Ethnicity',
                    race_3 = "Race",
                    parent_education = "Parent Education",
                    combined_income = "Household Income", 
                    GMV = 'cGM', 
                    WMV = 'WM', 
                    sGMV = 'sGM', 
                    Ventricles = 'CSF', 
                    euler = 'Motion (Euler)') %>%
getDescriptionStatsBy(age, 
                      sex,
                      puberty_stage,
                      ethnicity,
                      race_3,
                      parent_education,
                      combined_income,
                      euler, 
                      GMV, 
                      WMV, 
                      sGMV, 
                      Ventricles,
                      add_total_col = TRUE, statistics=FALSE, show_all_values=TRUE,
                      digits=2,
                      by = anova_group)
GMV_table
```

Make Demo Tables
```{r}
WMV_table <- all_WMV_data %>%
  set_column_labels(age = "Age (Years)",
                    sex = "Sex",
                    puberty_stage = "Pubertal Stage", 
                    ethnicity = 'Ethnicity',
                    race_3 = "Race",
                    parent_education = "Parent Education",
                    combined_income = "Household Income", 
                    GMV = 'cGM', 
                    WMV = 'WM', 
                    sGMV = 'sGM', 
                    Ventricles = 'CSF', 
                    euler = 'Motion (Euler)') %>%
getDescriptionStatsBy(age, 
                      sex,
                      puberty_stage,
                      ethnicity,
                      race_3,
                      parent_education,
                      combined_income,
                      euler, 
                      GMV, 
                      WMV, 
                      sGMV, 
                      Ventricles,
                      add_total_col = TRUE, statistics=FALSE, show_all_values=TRUE,
                      digits=2,
                      by = anova_group)
WMV_table
```

Make Demo Tables
```{r}
sGMV_table <- all_sGMV_data %>%
  set_column_labels(age = "Age (Years)",
                    sex = "Sex",
                    puberty_stage = "Pubertal Stage", 
                    ethnicity = 'Ethnicity',
                    race_3 = "Race",
                    parent_education = "Parent Education",
                    combined_income = "Household Income", 
                    GMV = 'cGM', 
                    WMV = 'WM', 
                    sGMV = 'sGM', 
                    Ventricles = 'CSF', 
                    euler = 'Motion (Euler)') %>%
getDescriptionStatsBy(age, 
                      sex,
                      puberty_stage,
                      ethnicity,
                      race_3,
                      parent_education,
                      combined_income,
                      euler, 
                      GMV, 
                      WMV, 
                      sGMV, 
                      Ventricles,
                      add_total_col = TRUE, statistics=FALSE, show_all_values=TRUE,
                      digits=2,
                      by = anova_group)
sGMV_table
```

Make Demo Tables
```{r}
vent_table <- all_vent_data %>%
  set_column_labels(age = "Age (Years)",
                    sex = "Sex",
                    puberty_stage = "Pubertal Stage", 
                    ethnicity = 'Ethnicity',
                    race_3 = "Race",
                    parent_education = "Parent Education",
                    combined_income = "Household Income", 
                    GMV = 'cGM', 
                    WMV = 'WM', 
                    sGMV = 'sGM', 
                    Ventricles = 'CSF', 
                    euler = 'Motion (Euler)') %>%
getDescriptionStatsBy(age, 
                      sex,
                      puberty_stage,
                      ethnicity,
                      race_3,
                      parent_education,
                      combined_income,
                      euler, 
                      GMV, 
                      WMV, 
                      sGMV, 
                      Ventricles,
                      add_total_col = TRUE, statistics=FALSE, show_all_values=TRUE,
                      digits=2,
                      by = anova_group)
vent_table
```

List out variables for each type of test
```{r}
anova_vs<- c('age', 'GMV', 'WMV', 'sGMV', 'Ventricles', 'parent_education', 
           'combined_income', 'puberty_stage', 'euler')
chi_vs<- c('sex', 'race_3', 'site_id', 'ethnicity')
```

Anova function
```{r}
run_anova_tests <- function(data, vars, group_var) {
  results <- data.frame(
    Variable = character(),
    Test_Type = character(),
    Omnibus_Stat = numeric(),
    P_Value = numeric(),
    Comparison = character(),
    Pairwise_P_Value = numeric(),
    stringsAsFactors = FALSE
  )
  
  for (var in vars) {
    if (is.numeric(data[[var]])) {
      # Perform ANOVA
      aov_model <- aov(data[[var]] ~ as.factor(data[[group_var]]))
      aov_summary <- summary(aov_model)
      omnibus_stat <- aov_summary[[1]][["F value"]][1]
      p_value <- aov_summary[[1]][["Pr(>F)"]][1]
      
      # Store omnibus ANOVA result
      results <- results %>%
        add_row(
          Variable = var,
          Test_Type = "ANOVA",
          Omnibus_Stat = omnibus_stat,
          P_Value = p_value,
          Comparison = NA,
          Pairwise_P_Value = NA
        )
      
      # Perform Tukey HSD for pairwise comparisons
      tukey_result <- TukeyHSD(aov_model)
      tukey_df <- as.data.frame(tukey_result[[1]])
      tukey_df$Comparison <- rownames(tukey_df)
      
      # Add pairwise comparisons to results
      pairwise_results <- tukey_df %>%
        select(Comparison, `p adj`) %>%
        rename(Pairwise_P_Value = `p adj`) %>%
        mutate(
          Variable = var,
          Test_Type = "ANOVA",
          Omnibus_Stat = NA,
          P_Value = NA
        )
      
      results <- bind_rows(results, pairwise_results)
    }
  }
  
  return(results)
}
```


Run ANOVA functions
```{r}
GMV_anova_results <- run_anova_tests(all_GMV_data, anova_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
WMV_anova_results <- run_anova_tests(all_WMV_data, anova_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
sGMV_anova_results <- run_anova_tests(all_sGMV_data, anova_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
vent_anova_results <- run_anova_tests(all_vent_data, anova_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
```

HTML:
```{r}
GMV_anova_results%>% kable(format = "html")
WMV_anova_results%>% kable(format = "html")
sGMV_anova_results%>% kable(format = "html")
vent_anova_results%>% kable(format = "html")
```

Do chi-square by hand because everything is a piece of shit 

GMV:
```{r warn.conflicts=F, quietly=T}
matchH_avg<-filter(all_GMV_data, anova_group %in% c("avg", "match_high"))
matchL_avg<-filter(all_GMV_data, anova_group %in% c("avg", "match_low"))
tailsH_avg<-filter(all_GMV_data, anova_group %in% c("avg", "tails_high"))
tailsL_avg<-filter(all_GMV_data, anova_group %in% c("avg", "tails_low"))
matchH_matchL<-filter(all_GMV_data, anova_group %in% c("match_high", "match_low"))
matchH_tailsH<-filter(all_GMV_data, anova_group %in% c("match_high", "tails_high"))
tailsL_matchH<-filter(all_GMV_data, anova_group %in% c("tails_low", "match_high"))
tailsH_matchL<-filter(all_GMV_data, anova_group %in% c("match_low", "tails_high"))
tailsL_matchL<-filter(all_GMV_data, anova_group %in% c("tails_low", "match_low"))
tailsL_tailsH<-filter(all_GMV_data, anova_group %in% c("tails_low", "tails_high"))

sex_om<- chisq.test(all_GMV_data$anova_group, all_GMV_data$sex)
sex1<-chisq.test(matchH_avg$anova_group, matchH_avg$sex)
sex2<-chisq.test(matchL_avg$anova_group, matchL_avg$sex)
sex3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$sex)
sex4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$sex)
sex5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$sex)
sex6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$sex)
sex7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$sex)
sex8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$sex)
sex9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$sex)
sex10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$sex)

GMV_sex_mult<-c(sex_om$statistic, sex_om$p.value, sex1$p.value, sex2$p.value, sex3$p.value, sex4$p.value, sex5$p.value, sex6$p.value,
                sex7$p.value, sex8$p.value, sex9$p.value, sex10$p.value)

ethnicity_om<- chisq.test(all_GMV_data$anova_group, all_GMV_data$ethnicity)
ethnicity1<-chisq.test(matchH_avg$anova_group, matchH_avg$ethnicity)
ethnicity2<-chisq.test(matchL_avg$anova_group, matchL_avg$ethnicity)
ethnicity3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$ethnicity)
ethnicity4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$ethnicity)
ethnicity5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$ethnicity)
ethnicity6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$ethnicity)
ethnicity7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$ethnicity)
ethnicity8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$ethnicity)
ethnicity9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$ethnicity)
ethnicity10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$ethnicity)

GMV_ethnicity_mult<-c(ethnicity_om$statistic, ethnicity_om$p.value, 
                      ethnicity1$p.value, ethnicity2$p.value, ethnicity3$p.value, ethnicity4$p.value, ethnicity5$p.value, ethnicity6$p.value,
                  ethnicity7$p.value, ethnicity8$p.value, ethnicity9$p.value, ethnicity10$p.value)

race_3_om<- chisq.test(all_GMV_data$anova_group, all_GMV_data$race_3)
race_31<-chisq.test(matchH_avg$anova_group, matchH_avg$race_3)
race_32<-chisq.test(matchL_avg$anova_group, matchL_avg$race_3)
race_33<-chisq.test(tailsH_avg$anova_group, tailsH_avg$race_3)
race_34<-chisq.test(tailsL_avg$anova_group, tailsL_avg$race_3)
race_35<-chisq.test(matchH_matchL$anova_group, matchH_matchL$race_3)
race_36<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$race_3)
race_37<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$race_3)
race_38<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$race_3)
race_39<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$race_3)
race_310<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$race_3)

GMV_race_3_mult<-c(race_3_om$statistic, race_3_om$p.value, race_31$p.value, race_32$p.value, race_33$p.value, race_34$p.value,
                   race_35$p.value, race_36$p.value,
                  race_37$p.value, race_38$p.value, race_39$p.value, race_310$p.value)

site_om<- chisq.test(all_GMV_data$anova_group, all_GMV_data$site_id)
site_id1<-chisq.test(matchH_avg$anova_group, matchH_avg$site_id)
site_id2<-chisq.test(matchL_avg$anova_group, matchL_avg$site_id)
site_id3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$site_id)
site_id4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$site_id)
site_id5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$site_id)
site_id6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$site_id)
site_id7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$site_id)
site_id8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$site_id)
site_id9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$site_id)
site_id10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$site_id)

GMV_site_id_mult<-c(site_om$statistic, site_om$p.value, site_id1$p.value, site_id2$p.value, site_id3$p.value, site_id4$p.value,
                    site_id5$p.value, site_id6$p.value,
                  site_id7$p.value, site_id8$p.value, site_id9$p.value, site_id10$p.value)
```

WMV:
```{r}
matchH_avg<-filter(all_WMV_data, anova_group %in% c("avg", "match_high"))
matchL_avg<-filter(all_WMV_data, anova_group %in% c("avg", "match_low"))
tailsH_avg<-filter(all_WMV_data, anova_group %in% c("avg", "tails_high"))
tailsL_avg<-filter(all_WMV_data, anova_group %in% c("avg", "tails_low"))
matchH_matchL<-filter(all_WMV_data, anova_group %in% c("match_high", "match_low"))
matchH_tailsH<-filter(all_WMV_data, anova_group %in% c("match_high", "tails_high"))
tailsL_matchH<-filter(all_WMV_data, anova_group %in% c("tails_low", "match_high"))
tailsH_matchL<-filter(all_WMV_data, anova_group %in% c("match_low", "tails_high"))
tailsL_matchL<-filter(all_WMV_data, anova_group %in% c("tails_low", "match_low"))
tailsL_tailsH<-filter(all_WMV_data, anova_group %in% c("tails_low", "tails_high"))

sex_om<- chisq.test(all_WMV_data$anova_group, all_WMV_data$sex)
sex1<-chisq.test(matchH_avg$anova_group, matchH_avg$sex)
sex2<-chisq.test(matchL_avg$anova_group, matchL_avg$sex)
sex3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$sex)
sex4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$sex)
sex5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$sex)
sex6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$sex)
sex7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$sex)
sex8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$sex)
sex9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$sex)
sex10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$sex)

WMV_sex_mult<-c(sex_om$statistic, sex_om$p.value, sex1$p.value, sex2$p.value, sex3$p.value, sex4$p.value, sex5$p.value, sex6$p.value,
                sex7$p.value, sex8$p.value, sex9$p.value, sex10$p.value)

ethnicity_om<- chisq.test(all_WMV_data$anova_group, all_WMV_data$ethnicity)
ethnicity1<-chisq.test(matchH_avg$anova_group, matchH_avg$ethnicity)
ethnicity2<-chisq.test(matchL_avg$anova_group, matchL_avg$ethnicity)
ethnicity3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$ethnicity)
ethnicity4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$ethnicity)
ethnicity5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$ethnicity)
ethnicity6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$ethnicity)
ethnicity7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$ethnicity)
ethnicity8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$ethnicity)
ethnicity9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$ethnicity)
ethnicity10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$ethnicity)

WMV_ethnicity_mult<-c(ethnicity_om$statistic, ethnicity_om$p.value, 
                      ethnicity1$p.value, ethnicity2$p.value, ethnicity3$p.value, ethnicity4$p.value, ethnicity5$p.value, ethnicity6$p.value,
                  ethnicity7$p.value, ethnicity8$p.value, ethnicity9$p.value, ethnicity10$p.value)

race_3_om<- chisq.test(all_WMV_data$anova_group, all_WMV_data$race_3)
race_31<-chisq.test(matchH_avg$anova_group, matchH_avg$race_3)
race_32<-chisq.test(matchL_avg$anova_group, matchL_avg$race_3)
race_33<-chisq.test(tailsH_avg$anova_group, tailsH_avg$race_3)
race_34<-chisq.test(tailsL_avg$anova_group, tailsL_avg$race_3)
race_35<-chisq.test(matchH_matchL$anova_group, matchH_matchL$race_3)
race_36<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$race_3)
race_37<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$race_3)
race_38<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$race_3)
race_39<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$race_3)
race_310<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$race_3)

WMV_race_3_mult<-c(race_3_om$statistic, race_3_om$p.value, race_31$p.value, race_32$p.value, race_33$p.value, race_34$p.value,
                   race_35$p.value, race_36$p.value,
                  race_37$p.value, race_38$p.value, race_39$p.value, race_310$p.value)

site_om<- chisq.test(all_WMV_data$anova_group, all_WMV_data$site_id)
site_id1<-chisq.test(matchH_avg$anova_group, matchH_avg$site_id)
site_id2<-chisq.test(matchL_avg$anova_group, matchL_avg$site_id)
site_id3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$site_id)
site_id4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$site_id)
site_id5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$site_id)
site_id6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$site_id)
site_id7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$site_id)
site_id8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$site_id)
site_id9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$site_id)
site_id10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$site_id)

WMV_site_id_mult<-c(site_om$statistic, site_om$p.value, site_id1$p.value, site_id2$p.value, site_id3$p.value, site_id4$p.value,
                    site_id5$p.value, site_id6$p.value,
                  site_id7$p.value, site_id8$p.value, site_id9$p.value, site_id10$p.value)
```

sGMV:
```{r}
matchH_avg<-filter(all_sGMV_data, anova_group %in% c("avg", "match_high"))
matchL_avg<-filter(all_sGMV_data, anova_group %in% c("avg", "match_low"))
tailsH_avg<-filter(all_sGMV_data, anova_group %in% c("avg", "tails_high"))
tailsL_avg<-filter(all_sGMV_data, anova_group %in% c("avg", "tails_low"))
matchH_matchL<-filter(all_sGMV_data, anova_group %in% c("match_high", "match_low"))
matchH_tailsH<-filter(all_sGMV_data, anova_group %in% c("match_high", "tails_high"))
tailsL_matchH<-filter(all_sGMV_data, anova_group %in% c("tails_low", "match_high"))
tailsH_matchL<-filter(all_sGMV_data, anova_group %in% c("match_low", "tails_high"))
tailsL_matchL<-filter(all_sGMV_data, anova_group %in% c("tails_low", "match_low"))
tailsL_tailsH<-filter(all_sGMV_data, anova_group %in% c("tails_low", "tails_high"))

sex_om<- chisq.test(all_sGMV_data$anova_group, all_sGMV_data$sex)
sex1<-chisq.test(matchH_avg$anova_group, matchH_avg$sex)
sex2<-chisq.test(matchL_avg$anova_group, matchL_avg$sex)
sex3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$sex)
sex4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$sex)
sex5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$sex)
sex6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$sex)
sex7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$sex)
sex8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$sex)
sex9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$sex)
sex10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$sex)

sGMV_sex_mult<-c(sex_om$statistic, sex_om$p.value, sex1$p.value, sex2$p.value, sex3$p.value, sex4$p.value, sex5$p.value, sex6$p.value,
                sex7$p.value, sex8$p.value, sex9$p.value, sex10$p.value)

ethnicity_om<- chisq.test(all_sGMV_data$anova_group, all_sGMV_data$ethnicity)
ethnicity1<-chisq.test(matchH_avg$anova_group, matchH_avg$ethnicity)
ethnicity2<-chisq.test(matchL_avg$anova_group, matchL_avg$ethnicity)
ethnicity3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$ethnicity)
ethnicity4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$ethnicity)
ethnicity5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$ethnicity)
ethnicity6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$ethnicity)
ethnicity7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$ethnicity)
ethnicity8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$ethnicity)
ethnicity9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$ethnicity)
ethnicity10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$ethnicity)

sGMV_ethnicity_mult<-c(ethnicity_om$statistic, ethnicity_om$p.value, 
                      ethnicity1$p.value, ethnicity2$p.value, ethnicity3$p.value, ethnicity4$p.value, ethnicity5$p.value, ethnicity6$p.value,
                  ethnicity7$p.value, ethnicity8$p.value, ethnicity9$p.value, ethnicity10$p.value)

race_3_om<- chisq.test(all_sGMV_data$anova_group, all_sGMV_data$race_3)
race_31<-chisq.test(matchH_avg$anova_group, matchH_avg$race_3)
race_32<-chisq.test(matchL_avg$anova_group, matchL_avg$race_3)
race_33<-chisq.test(tailsH_avg$anova_group, tailsH_avg$race_3)
race_34<-chisq.test(tailsL_avg$anova_group, tailsL_avg$race_3)
race_35<-chisq.test(matchH_matchL$anova_group, matchH_matchL$race_3)
race_36<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$race_3)
race_37<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$race_3)
race_38<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$race_3)
race_39<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$race_3)
race_310<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$race_3)

sGMV_race_3_mult<-c(race_3_om$statistic, race_3_om$p.value, race_31$p.value, race_32$p.value, race_33$p.value, race_34$p.value,
                   race_35$p.value, race_36$p.value,
                  race_37$p.value, race_38$p.value, race_39$p.value, race_310$p.value)

site_om<- chisq.test(all_sGMV_data$anova_group, all_sGMV_data$site_id)
site_id1<-chisq.test(matchH_avg$anova_group, matchH_avg$site_id)
site_id2<-chisq.test(matchL_avg$anova_group, matchL_avg$site_id)
site_id3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$site_id)
site_id4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$site_id)
site_id5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$site_id)
site_id6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$site_id)
site_id7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$site_id)
site_id8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$site_id)
site_id9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$site_id)
site_id10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$site_id)

sGMV_site_id_mult<-c(site_om$statistic, site_om$p.value, site_id1$p.value, site_id2$p.value, site_id3$p.value, site_id4$p.value,
                    site_id5$p.value, site_id6$p.value,
                  site_id7$p.value, site_id8$p.value, site_id9$p.value, site_id10$p.value)
```

vent:
```{r}
matchH_avg<-filter(all_vent_data, anova_group %in% c("avg", "match_high"))
matchL_avg<-filter(all_vent_data, anova_group %in% c("avg", "match_low"))
tailsH_avg<-filter(all_vent_data, anova_group %in% c("avg", "tails_high"))
tailsL_avg<-filter(all_vent_data, anova_group %in% c("avg", "tails_low"))
matchH_matchL<-filter(all_vent_data, anova_group %in% c("match_high", "match_low"))
matchH_tailsH<-filter(all_vent_data, anova_group %in% c("match_high", "tails_high"))
tailsL_matchH<-filter(all_vent_data, anova_group %in% c("tails_low", "match_high"))
tailsH_matchL<-filter(all_vent_data, anova_group %in% c("match_low", "tails_high"))
tailsL_matchL<-filter(all_vent_data, anova_group %in% c("tails_low", "match_low"))
tailsL_tailsH<-filter(all_vent_data, anova_group %in% c("tails_low", "tails_high"))

sex_om<- chisq.test(all_vent_data$anova_group, all_vent_data$sex)
sex1<-chisq.test(matchH_avg$anova_group, matchH_avg$sex)
sex2<-chisq.test(matchL_avg$anova_group, matchL_avg$sex)
sex3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$sex)
sex4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$sex)
sex5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$sex)
sex6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$sex)
sex7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$sex)
sex8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$sex)
sex9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$sex)
sex10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$sex)

vent_sex_mult<-c(sex_om$statistic, sex_om$p.value, sex1$p.value, sex2$p.value, sex3$p.value, sex4$p.value, sex5$p.value, sex6$p.value,
                sex7$p.value, sex8$p.value, sex9$p.value, sex10$p.value)

ethnicity_om<- chisq.test(all_vent_data$anova_group, all_vent_data$ethnicity)
ethnicity1<-chisq.test(matchH_avg$anova_group, matchH_avg$ethnicity)
ethnicity2<-chisq.test(matchL_avg$anova_group, matchL_avg$ethnicity)
ethnicity3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$ethnicity)
ethnicity4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$ethnicity)
ethnicity5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$ethnicity)
ethnicity6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$ethnicity)
ethnicity7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$ethnicity)
ethnicity8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$ethnicity)
ethnicity9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$ethnicity)
ethnicity10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$ethnicity)

vent_ethnicity_mult<-c(ethnicity_om$statistic, ethnicity_om$p.value, 
                      ethnicity1$p.value, ethnicity2$p.value, ethnicity3$p.value, ethnicity4$p.value, ethnicity5$p.value, ethnicity6$p.value,
                  ethnicity7$p.value, ethnicity8$p.value, ethnicity9$p.value, ethnicity10$p.value)

race_3_om<- chisq.test(all_vent_data$anova_group, all_vent_data$race_3)
race_31<-chisq.test(matchH_avg$anova_group, matchH_avg$race_3)
race_32<-chisq.test(matchL_avg$anova_group, matchL_avg$race_3)
race_33<-chisq.test(tailsH_avg$anova_group, tailsH_avg$race_3)
race_34<-chisq.test(tailsL_avg$anova_group, tailsL_avg$race_3)
race_35<-chisq.test(matchH_matchL$anova_group, matchH_matchL$race_3)
race_36<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$race_3)
race_37<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$race_3)
race_38<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$race_3)
race_39<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$race_3)
race_310<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$race_3)

vent_race_3_mult<-c(race_3_om$statistic, race_3_om$p.value, race_31$p.value, race_32$p.value, race_33$p.value, race_34$p.value,
                   race_35$p.value, race_36$p.value,
                  race_37$p.value, race_38$p.value, race_39$p.value, race_310$p.value)

site_om<- chisq.test(all_vent_data$anova_group, all_vent_data$site_id)
site_id1<-chisq.test(matchH_avg$anova_group, matchH_avg$site_id)
site_id2<-chisq.test(matchL_avg$anova_group, matchL_avg$site_id)
site_id3<-chisq.test(tailsH_avg$anova_group, tailsH_avg$site_id)
site_id4<-chisq.test(tailsL_avg$anova_group, tailsL_avg$site_id)
site_id5<-chisq.test(matchH_matchL$anova_group, matchH_matchL$site_id)
site_id6<-chisq.test(matchH_tailsH$anova_group, matchH_tailsH$site_id)
site_id7<-chisq.test(tailsL_matchH$anova_group, tailsL_matchH$site_id)
site_id8<-chisq.test(tailsH_matchL$anova_group, tailsH_matchL$site_id)
site_id9<-chisq.test(tailsL_matchL$anova_group, tailsL_matchL$site_id)
site_id10<-chisq.test(tailsL_tailsH$anova_group, tailsL_tailsH$site_id)

vent_site_id_mult<-c(site_om$statistic, site_om$p.value, site_id1$p.value, site_id2$p.value, site_id3$p.value, site_id4$p.value,
                    site_id5$p.value, site_id6$p.value,
                  site_id7$p.value, site_id8$p.value, site_id9$p.value, site_id10$p.value)
```

Put them together 
```{r}
GMV_mult<- data.frame(rbind(GMV_sex_mult, GMV_ethnicity_mult, GMV_race_3_mult, GMV_site_id_mult))
WMV_mult<- data.frame(rbind(WMV_sex_mult, WMV_ethnicity_mult, WMV_race_3_mult, WMV_site_id_mult))
sGMV_mult<- data.frame(rbind(sGMV_sex_mult, sGMV_ethnicity_mult, sGMV_race_3_mult, sGMV_site_id_mult))
vent_mult<- data.frame(rbind(vent_sex_mult, vent_ethnicity_mult, vent_race_3_mult, vent_site_id_mult))
```

NOW do it with centered data: 
```{r}
centered_GMV_data<- all_GMV_data%>%
  mutate(c_GMV = GMV - mean(GMV, na.rm=T))%>%
  mutate(c_WMV = WMV - mean(WMV, na.rm=T))%>%
  mutate(c_sGMV = sGMV - mean(sGMV, na.rm=T))%>%
  mutate(c_vent = Ventricles - mean(Ventricles, na.rm=T))%>%
  mutate(c_age = age - mean(age, na.rm=T))%>%
  mutate(c_income = combined_income - mean(combined_income, na.rm=T))%>%
  mutate(c_education = parent_education - mean(parent_education, na.rm=T))%>%
  mutate(c_euler = euler - mean(euler, na.rm=T))%>%
  mutate(c_puberty = puberty_stage - mean(puberty_stage, na.rm=T))%>%
  select(starts_with(c('subjectkey', 'c_', 'anova_group')))

centered_WMV_data<- all_WMV_data%>%
  mutate(c_GMV = GMV - mean(GMV, na.rm=T))%>%
  mutate(c_WMV = WMV - mean(WMV, na.rm=T))%>%
  mutate(c_sGMV = sGMV - mean(sGMV, na.rm=T))%>%
  mutate(c_vent = Ventricles - mean(Ventricles, na.rm=T))%>%
  mutate(c_age = age - mean(age, na.rm=T))%>%
  mutate(c_income = combined_income - mean(combined_income, na.rm=T))%>%
  mutate(c_education = parent_education - mean(parent_education, na.rm=T))%>%
  mutate(c_euler = euler - mean(euler, na.rm=T))%>%
  mutate(c_puberty = puberty_stage - mean(puberty_stage, na.rm=T))%>%
  select(starts_with(c('subjectkey', 'c_', 'anova_group')))

centered_sGMV_data<- all_sGMV_data%>%
  mutate(c_GMV = GMV - mean(GMV, na.rm=T))%>%
  mutate(c_WMV = WMV - mean(WMV, na.rm=T))%>%
  mutate(c_sGMV = sGMV - mean(sGMV, na.rm=T))%>%
  mutate(c_vent = Ventricles - mean(Ventricles, na.rm=T))%>%
  mutate(c_age = age - mean(age, na.rm=T))%>%
  mutate(c_income = combined_income - mean(combined_income, na.rm=T))%>%
  mutate(c_education = parent_education - mean(parent_education, na.rm=T))%>%
  mutate(c_euler = euler - mean(euler, na.rm=T))%>%
  mutate(c_puberty = puberty_stage - mean(puberty_stage, na.rm=T))%>%
  select(starts_with(c('subjectkey', 'c_', 'anova_group')))

centered_vent_data<- all_vent_data%>%
  mutate(c_GMV = GMV - mean(GMV, na.rm=T))%>%
  mutate(c_WMV = WMV - mean(WMV, na.rm=T))%>%
  mutate(c_sGMV = sGMV - mean(sGMV, na.rm=T))%>%
  mutate(c_vent = Ventricles - mean(Ventricles, na.rm=T))%>%
  mutate(c_age = age - mean(age, na.rm=T))%>%
  mutate(c_income = combined_income - mean(combined_income, na.rm=T))%>%
  mutate(c_education = parent_education - mean(parent_education, na.rm=T))%>%
  mutate(c_euler = euler - mean(euler, na.rm=T))%>%
  mutate(c_puberty = puberty_stage - mean(puberty_stage, na.rm=T))%>%
  select(starts_with(c('subjectkey', 'c_', 'anova_group')))
```

new v's
```{r}
centered_vs<- c('c_GMV', 'c_WMV', 'c_sGMV', 'c_vent', 'c_age', 'c_income', 'c_education', 'c_euler', 'c_puberty')

```

Run ANOVA functions
```{r}
c_GMV_anova_results <- run_anova_tests(centered_GMV_data, centered_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
c_WMV_anova_results <- run_anova_tests(centered_WMV_data, centered_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
c_sGMV_anova_results <- run_anova_tests(centered_sGMV_data, centered_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
c_vent_anova_results <- run_anova_tests(centered_vent_data, centered_vs, "anova_group")%>%
  pivot_wider(names_from=Comparison, values_from=Pairwise_P_Value)
```

HTML:
```{r}
c_GMV_anova_results%>% kable(format = "html")
c_WMV_anova_results%>% kable(format = "html")
c_sGMV_anova_results%>% kable(format = "html")
c_vent_anova_results%>% kable(format = "html")
```
```{r}
anova(c)
```