---
title: "Topography Matching Notebook Step 2"
output:
  html_document:
    df_print: paged
---

This R Notebook runs multivariate multiple regression to model the effects of brain tissue type group on cognitive outcomes using dimensional, tail sampled, and propensity matched modeling strategies. 

-----------------------------------
Set Up
-----------------------------------

First, install necessary packages.
```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(lm.beta)
library(ggpubr)
library(bayesbio)
library(lavaan)
library(knitr) 
library(gt)
```

Specify that select function should be pulled from dplyr
```{r}
select <- dplyr::select
recode <- dplyr::recode
```

Next, log into PennBox, and set working directory the ABCD directory.
```{r}
box_auth()

box_setwd('167848222541')
```

Load in matched network data:
```{r}
match_vent_data<-box_read('1438682877497', fread=TRUE)
match_sGMV_data<-box_read('1438681749218', fread=TRUE)
match_WMV_data<-box_read('1438687945370', fread=TRUE)
match_GMV_data<-box_read('1438677748369', fread=TRUE)
```
Now, we will add in additional data to see if our groups differ meaningfully on cognitive outcomes.


Read in Cognitive Data 
```{r}
cog_data<-box_read('1022619576971', fread=TRUE)
cog_data<-as_tibble(cog_data)%>%
  slice(2:n()) %>% #drop the first row, which contains the variable definitions
  dplyr::select(-collection_id,-abcd_tbss01_id,-dataset_id,-interview_date) %>% 
  dplyr::select_if(~!(all(is.na(.)) | all(. == ""))) %>% #get rid of totally empty columns
  mutate(across(everything(), ~ifelse(.=="", NA, as.character(.)))) #recode blank rows as "NA" 

cog_data_short<- cog_data %>%
  dplyr::select(ends_with(c("subjectkey", "eventname", "uncorrected")))%>%
  filter(eventname=='baseline_year_1_arm_1')
```


and merge into data:
```{r}
GMV_test_data<- merge(match_GMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey","subclass", "distance", "weights")),as.numeric)

WMV_test_data<- merge(match_WMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey","subclass", "distance", "weights")),as.numeric)

sGMV_test_data<- merge(match_WMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey","subclass", "distance", "weights")),as.numeric)

vent_test_data<- merge(match_vent_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey","subclass", "distance", "weights")),as.numeric)
```

```{r}
psych::describe(GMV_test_data)
psych::describe(WMV_test_data)
psych::describe(sGMV_test_data)
psych::describe(vent_test_data)
```
Finally, load in unmatched network data: 
```{r}
unmatched_GMV_data<-box_read('1442236849436', fread=TRUE)
unmatched_WMV_data<-box_read('1442223376606', fread=TRUE)
unmatched_sGMV_data<-box_read('1442239979732', fread=TRUE)
unmatched_vent_data<-box_read('1442240154828', fread=TRUE)
```

and merge into data:
```{r}
GMV_test_data2<- merge(unmatched_GMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)

WMV_test_data2<- merge(unmatched_WMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)

sGMV_test_data2<- merge(unmatched_sGMV_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)

vent_test_data2<- merge(unmatched_vent_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)
```

```{r}
psych::describe(GMV_test_data2)
psych::describe(WMV_test_data2)
psych::describe(sGMV_test_data2)
psych::describe(vent_test_data2)
```
Load in dimensional network data: 
```{r}
all_dimensional_data<-box_read('1442204075893', fread=TRUE)

all_dimensional_data<- merge(all_dimensional_data, cog_data_short, by='subjectkey')%>%
  mutate_at(vars(-c("subjectkey")),as.numeric)
```

```{r}
psych::describe(all_dimensional_data)
```

-----------------------------------
Specify Models
-----------------------------------

Specify group-based models for Lavaan: 
(these can be used with different data sets for both tail sampled and pm'd models)
```{r}
cog_group_models<- 
'
nihtbx_picvocab_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_flanker_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_list_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_cardsort_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_pattern_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picture_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_reading_uncorrected ~ group + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picvocab_uncorrected ~~ nihtbx_flanker_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_picture_uncorrected ~~ nihtbx_reading_uncorrected
'
```

Specify dimensional models for Lavaan: 
```{r}
cog_gmv_model<- 
'
nihtbx_picvocab_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_flanker_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_list_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_cardsort_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_pattern_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picture_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_reading_uncorrected ~ GMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picvocab_uncorrected ~~ nihtbx_flanker_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_picture_uncorrected ~~ nihtbx_reading_uncorrected
'
cog_wmv_model<- 
'
nihtbx_picvocab_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_flanker_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_list_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_cardsort_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_pattern_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picture_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_reading_uncorrected ~ WMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picvocab_uncorrected ~~ nihtbx_flanker_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_picture_uncorrected ~~ nihtbx_reading_uncorrected
'
cog_sgmv_model<- 
'
nihtbx_picvocab_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_flanker_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_list_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_cardsort_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_pattern_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picture_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_reading_uncorrected ~ sGMV + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picvocab_uncorrected ~~ nihtbx_flanker_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_picture_uncorrected ~~ nihtbx_reading_uncorrected
'
cog_vent_model<- 
'
nihtbx_picvocab_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_flanker_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_list_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_cardsort_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_pattern_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picture_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_reading_uncorrected ~ Ventricles + age + sex + site_id + puberty_stage + ethnicity + race_3 + parent_education + combined_income
nihtbx_picvocab_uncorrected ~~ nihtbx_flanker_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_picvocab_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_list_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_flanker_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_cardsort_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_list_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_pattern_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_cardsort_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_picture_uncorrected
nihtbx_pattern_uncorrected ~~ nihtbx_reading_uncorrected
nihtbx_picture_uncorrected ~~ nihtbx_reading_uncorrected
'
```

-----------------------------------
Evaluate Fit
-----------------------------------
Evaluate Fit in Matched Data 
```{r}
matched_GMV_fit <- sem(cog_group_models, data=GMV_test_data, missing="ML", estimator="MLR")
#summary(matched_GMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

matched_WMV_fit <- sem(cog_group_models, data=WMV_test_data, missing="ML", estimator="MLR")
#summary(matched_WMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

matched_sGMV_fit <- sem(cog_group_models, data=sGMV_test_data, missing="ML", estimator="MLR")
#summary(matched_sGMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

matched_vent_fit <- sem(cog_group_models, data=vent_test_data, missing="ML", estimator="MLR")
#summary(matched_vent_fit, standardized = T, fit = F, rsquare = T, ci = T)
```

Evaluate Fit in Tail-Sampled Data 
```{r}
tails_GMV_fit <- sem(cog_group_models, data=GMV_test_data2, missing="ML", estimator="MLR")
#summary(tails_GMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

tails_WMV_fit <- sem(cog_group_models, data=WMV_test_data2, missing="ML", estimator="MLR")
#summary(tails_WMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

tails_sGMV_fit <- sem(cog_group_models, data=sGMV_test_data2, missing="ML", estimator="MLR")
#summary(tails_sGMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

tails_vent_fit <- sem(cog_group_models, data=vent_test_data2, missing="ML", estimator="MLR")
#summary(tails_vent_fit, standardized = T, fit = F, rsquare = T, ci = T)
```


Evaluate Fit in Tail-Sampled Data 
```{r}
dim_GMV_fit <- sem(cog_gmv_model, data=all_dimensional_data, missing="ML", estimator="MLR")
#summary(tails_GMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

dim_WMV_fit <- sem(cog_wmv_model, data=all_dimensional_data, missing="ML", estimator="MLR")
#summary(tails_WMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

dim_sGMV_fit <- sem(cog_sgmv_model, data=all_dimensional_data, missing="ML", estimator="MLR")
#summary(tails_sGMV_fit, standardized = T, fit = F, rsquare = T, ci = T)

dim_vent_fit <- sem(cog_vent_model, data=all_dimensional_data, missing="ML", estimator="MLR")
#summary(tails_vent_fit, standardized = T, fit = F, rsquare = T, ci = T)
```

Now FDR correct + add a variable for model type 
```{r}
matched_GMV_fdr<- parameterEstimates(matched_GMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'matched')

matched_WMV_fdr<- parameterEstimates(matched_WMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'matched')

matched_sGMV_fdr<- parameterEstimates(matched_sGMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'matched')

matched_vent_fdr<- parameterEstimates(matched_vent_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'matched')

dim_GMV_fdr<- parameterEstimates(dim_GMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'dim')

dim_WMV_fdr<- parameterEstimates(dim_WMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'dim')

dim_sGMV_fdr<- parameterEstimates(dim_sGMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'dim')

dim_vent_fdr<- parameterEstimates(dim_vent_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'dim')

tails_GMV_fdr<- parameterEstimates(tails_GMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'tails')

tails_WMV_fdr<- parameterEstimates(tails_WMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'tails')

tails_sGMV_fdr<- parameterEstimates(tails_sGMV_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'tails')

tails_vent_fdr<- parameterEstimates(tails_vent_fit, standardized = TRUE)%>%
  filter(op == "~")%>%
  select(lhs, rhs, est, se, pvalue, std.all)%>%
  mutate(ps_fdr= (p.adjust.nlp(pvalue, method='fdr', n=108)))%>%
  mutate(type = 'tails')
```

-----------------------------------
Format Results
-----------------------------------

GMV:
```{r}
#Format dimensionl results 
dim_GMV_html<- dim_GMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

dim_GMV_html$formatted_raw_est <- paste0(round(dim_GMV_html$est,2), ", (", round(dim_GMV_html$se,2), ")")
dim_GMV_html$formatted_std_est <- paste0(round(dim_GMV_html$std.all,2), dim_GMV_html$significance)

dim_GMV_html <- dim_GMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Dimensional Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format tail-sampled results
tails_GMV_html<- tails_GMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

tails_GMV_html$formatted_raw_est <- paste0(round(tails_GMV_html$est,2), ", (", round(tails_GMV_html$se,2), ")")
tails_GMV_html$formatted_std_est <- paste0(round(tails_GMV_html$std.all,2), tails_GMV_html$significance)

tails_GMV_html<- tails_GMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Tail-Sampled Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format matched results
matched_GMV_html<- matched_GMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

matched_GMV_html$formatted_raw_est <- paste0(round(matched_GMV_html$est,2), ", (", round(matched_GMV_html$se,2), ")")
matched_GMV_html$formatted_std_est <- paste0(round(matched_GMV_html$std.all,2), matched_GMV_html$significance)

matched_GMV_html <- matched_GMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model= 'Propensity Matched Models')%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Combine results, rename rhs
combined_GMV_html<- rbind(dim_GMV_html, tails_GMV_html, matched_GMV_html)%>%
  mutate(rhs = recode(rhs, "GMV" = "cGM", "age" = "Age", "sex" = "Sex", "site_id" = "Site ID", "puberty_stage" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race_3" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))

#Create a formatted regression table 
GMV_regression_table <- combined_GMV_html %>%
  gt(groupname_col = "model", rowname_col = "rhs") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    nihtbx_picvocab_uncorrected_formatted_raw_est = "Raw", nihtbx_picvocab_uncorrected_formatted_std_est = "Standardized",
    nihtbx_flanker_uncorrected_formatted_raw_est = "Raw", nihtbx_flanker_uncorrected_formatted_std_est = "Standardized",
    nihtbx_list_uncorrected_formatted_std_est = "Raw", nihtbx_list_uncorrected_formatted_std_est = "Standardized",
    nihtbx_cardsort_uncorrected_formatted_raw_est = "Raw", nihtbx_cardsort_uncorrected_formatted_std_est = "Standardized",
    nihtbx_pattern_uncorrected_formatted_raw_est = "Raw", nihtbx_pattern_uncorrected_formatted_std_est = "Standardized",
    nihtbx_picture_uncorrected_formatted_raw_est = "Raw", nihtbx_picture_uncorrected_formatted_std_est = "Standardized", 
    nihtbx_reading_uncorrected_formatted_raw_est = "Raw", nihtbx_reading_uncorrected_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Language",
    columns = c(nihtbx_picvocab_uncorrected_formatted_raw_est, nihtbx_picvocab_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Inhibitory Control",
    columns = c(nihtbx_flanker_uncorrected_formatted_raw_est, nihtbx_flanker_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Cognitive Flexibility",
    columns = c(nihtbx_list_uncorrected_formatted_raw_est, nihtbx_list_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Working Memory",
    columns = c(nihtbx_cardsort_uncorrected_formatted_raw_est, nihtbx_cardsort_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Processing Speed",
    columns = c(nihtbx_pattern_uncorrected_formatted_raw_est, nihtbx_pattern_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Episodic Memory",
    columns = c(nihtbx_picture_uncorrected_formatted_raw_est, nihtbx_picture_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Reading",
    columns = c(nihtbx_reading_uncorrected_formatted_raw_est, nihtbx_reading_uncorrected_formatted_std_est)
  ) %>%
  row_group_order(groups = c("Dimensional Models", "Tail-Sampled Models", "Propensity Matched Models")) # Order models if necessary

# Save the table as an HTML file
#GMV_regression_table %>%
  #gtsave("FINAL_REGRESSION_TABLES/HTML/cog_GMV_table.html")
```

WMV:
```{r}
#Format dimensionl results 
dim_WMV_html<- dim_WMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

dim_WMV_html$formatted_raw_est <- paste0(round(dim_WMV_html$est,2), ", (", round(dim_WMV_html$se,2), ")")
dim_WMV_html$formatted_std_est <- paste0(round(dim_WMV_html$std.all,2), dim_WMV_html$significance)

dim_WMV_html <- dim_WMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Dimensional Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format tail-sampled results
tails_WMV_html<- tails_WMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

tails_WMV_html$formatted_raw_est <- paste0(round(tails_WMV_html$est,2), ", (", round(tails_WMV_html$se,2), ")")
tails_WMV_html$formatted_std_est <- paste0(round(tails_WMV_html$std.all,2), tails_WMV_html$significance)

tails_WMV_html<- tails_WMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Tail-Sampled Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format matched results
matched_WMV_html<- matched_WMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

matched_WMV_html$formatted_raw_est <- paste0(round(matched_WMV_html$est,2), ", (", round(matched_WMV_html$se,2), ")")
matched_WMV_html$formatted_std_est <- paste0(round(matched_WMV_html$std.all,2), matched_WMV_html$significance)

matched_WMV_html <- matched_WMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model= 'Propensity Matched Models')%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Combine results, rename rhs
combined_WMV_html<- rbind(dim_WMV_html, tails_WMV_html, matched_WMV_html)%>%
  mutate(rhs = recode(rhs, "WMV" = "WM", "age" = "Age", "sex" = "Sex", "site_id" = "Site ID", "puberty_stage" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race_3" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))

#Create a formatted regression table 
WMV_regression_table <- combined_WMV_html %>%
  gt(groupname_col = "model", rowname_col = "rhs") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    nihtbx_picvocab_uncorrected_formatted_raw_est = "Raw", nihtbx_picvocab_uncorrected_formatted_std_est = "Standardized",
    nihtbx_flanker_uncorrected_formatted_raw_est = "Raw", nihtbx_flanker_uncorrected_formatted_std_est = "Standardized",
    nihtbx_list_uncorrected_formatted_std_est = "Raw", nihtbx_list_uncorrected_formatted_std_est = "Standardized",
    nihtbx_cardsort_uncorrected_formatted_raw_est = "Raw", nihtbx_cardsort_uncorrected_formatted_std_est = "Standardized",
    nihtbx_pattern_uncorrected_formatted_raw_est = "Raw", nihtbx_pattern_uncorrected_formatted_std_est = "Standardized",
    nihtbx_picture_uncorrected_formatted_raw_est = "Raw", nihtbx_picture_uncorrected_formatted_std_est = "Standardized", 
    nihtbx_reading_uncorrected_formatted_raw_est = "Raw", nihtbx_reading_uncorrected_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Language",
    columns = c(nihtbx_picvocab_uncorrected_formatted_raw_est, nihtbx_picvocab_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Inhibitory Control",
    columns = c(nihtbx_flanker_uncorrected_formatted_raw_est, nihtbx_flanker_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Cognitive Flexibility",
    columns = c(nihtbx_list_uncorrected_formatted_raw_est, nihtbx_list_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Working Memory",
    columns = c(nihtbx_cardsort_uncorrected_formatted_raw_est, nihtbx_cardsort_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Processing Speed",
    columns = c(nihtbx_pattern_uncorrected_formatted_raw_est, nihtbx_pattern_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Episodic Memory",
    columns = c(nihtbx_picture_uncorrected_formatted_raw_est, nihtbx_picture_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Reading",
    columns = c(nihtbx_reading_uncorrected_formatted_raw_est, nihtbx_reading_uncorrected_formatted_std_est)
  ) %>%
  row_group_order(groups = c("Dimensional Models", "Tail-Sampled Models", "Propensity Matched Models")) # Order models if necessary

# Save the table as an HTML file
#WMV_regression_table %>%
 # gtsave("FINAL_REGRESSION_TABLES/HTML/cog_WMV_table.html")
```

sGMV:
```{r}
#Format dimensionl results 
dim_sGMV_html<- dim_sGMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

dim_sGMV_html$formatted_raw_est <- paste0(round(dim_sGMV_html$est,2), ", (", round(dim_sGMV_html$se,2), ")")
dim_sGMV_html$formatted_std_est <- paste0(round(dim_sGMV_html$std.all,2), dim_sGMV_html$significance)

dim_sGMV_html <- dim_sGMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Dimensional Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format tail-sampled results
tails_sGMV_html<- tails_sGMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

tails_sGMV_html$formatted_raw_est <- paste0(round(tails_sGMV_html$est,2), ", (", round(tails_sGMV_html$se,2), ")")
tails_sGMV_html$formatted_std_est <- paste0(round(tails_sGMV_html$std.all,2), tails_sGMV_html$significance)

tails_sGMV_html<- tails_sGMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Tail-Sampled Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format matched results
matched_sGMV_html<- matched_sGMV_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

matched_sGMV_html$formatted_raw_est <- paste0(round(matched_sGMV_html$est,2), ", (", round(matched_sGMV_html$se,2), ")")
matched_sGMV_html$formatted_std_est <- paste0(round(matched_sGMV_html$std.all,2), matched_sGMV_html$significance)

matched_sGMV_html <- matched_sGMV_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model= 'Propensity Matched Models')%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Combine results, rename rhs
combined_sGMV_html<- rbind(dim_sGMV_html, tails_sGMV_html, matched_sGMV_html)%>%
  mutate(rhs = recode(rhs, "sGMV" = "sGM", "age" = "Age", "sex" = "Sex", "site_id" = "Site ID", "puberty_stage" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race_3" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))

#Create a formatted regression table 
sGMV_regression_table <- combined_sGMV_html %>%
  gt(groupname_col = "model", rowname_col = "rhs") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    nihtbx_picvocab_uncorrected_formatted_raw_est = "Raw", nihtbx_picvocab_uncorrected_formatted_std_est = "Standardized",
    nihtbx_flanker_uncorrected_formatted_raw_est = "Raw", nihtbx_flanker_uncorrected_formatted_std_est = "Standardized",
    nihtbx_list_uncorrected_formatted_std_est = "Raw", nihtbx_list_uncorrected_formatted_std_est = "Standardized",
    nihtbx_cardsort_uncorrected_formatted_raw_est = "Raw", nihtbx_cardsort_uncorrected_formatted_std_est = "Standardized",
    nihtbx_pattern_uncorrected_formatted_raw_est = "Raw", nihtbx_pattern_uncorrected_formatted_std_est = "Standardized",
    nihtbx_picture_uncorrected_formatted_raw_est = "Raw", nihtbx_picture_uncorrected_formatted_std_est = "Standardized", 
    nihtbx_reading_uncorrected_formatted_raw_est = "Raw", nihtbx_reading_uncorrected_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Language",
    columns = c(nihtbx_picvocab_uncorrected_formatted_raw_est, nihtbx_picvocab_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Inhibitory Control",
    columns = c(nihtbx_flanker_uncorrected_formatted_raw_est, nihtbx_flanker_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Cognitive Flexibility",
    columns = c(nihtbx_list_uncorrected_formatted_raw_est, nihtbx_list_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Working Memory",
    columns = c(nihtbx_cardsort_uncorrected_formatted_raw_est, nihtbx_cardsort_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Processing Speed",
    columns = c(nihtbx_pattern_uncorrected_formatted_raw_est, nihtbx_pattern_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Episodic Memory",
    columns = c(nihtbx_picture_uncorrected_formatted_raw_est, nihtbx_picture_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Reading",
    columns = c(nihtbx_reading_uncorrected_formatted_raw_est, nihtbx_reading_uncorrected_formatted_std_est)
  ) %>%
  row_group_order(groups = c("Dimensional Models", "Tail-Sampled Models", "Propensity Matched Models")) # Order models if necessary

# Save the table as an HTML file
#sGMV_regression_table %>%
  #gtsave("FINAL_REGRESSION_TABLES/HTML/cog_sGMV_table.html")
```

Vent:
```{r}
#Format dimensionl results 
dim_vent_html<- dim_vent_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

dim_vent_html$formatted_raw_est <- paste0(round(dim_vent_html$est,2), ", (", round(dim_vent_html$se,2), ")")
dim_vent_html$formatted_std_est <- paste0(round(dim_vent_html$std.all,2), dim_vent_html$significance)

dim_vent_html <- dim_vent_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Dimensional Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format tail-sampled results
tails_vent_html<- tails_vent_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

tails_vent_html$formatted_raw_est <- paste0(round(tails_vent_html$est,2), ", (", round(tails_vent_html$se,2), ")")
tails_vent_html$formatted_std_est <- paste0(round(tails_vent_html$std.all,2), tails_vent_html$significance)

tails_vent_html<- tails_vent_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model = "Tail-Sampled Models")%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Format matched results
matched_vent_html<- matched_vent_fdr %>%
  mutate(significance = case_when(
    ps_fdr < 0.001 ~ '***',
    ps_fdr < 0.01  ~ '**',
    ps_fdr < 0.05  ~ '*',
    ps_fdr < 0.10 ~ '†', 
    TRUE            ~ ''  # ns for not significant
  ))

matched_vent_html$formatted_raw_est <- paste0(round(matched_vent_html$est,2), ", (", round(matched_vent_html$se,2), ")")
matched_vent_html$formatted_std_est <- paste0(round(matched_vent_html$std.all,2), matched_vent_html$significance)

matched_vent_html <- matched_vent_html %>%
  select(lhs, rhs, formatted_raw_est, formatted_std_est)%>%
  mutate(model= 'Propensity Matched Models')%>%
  pivot_longer(cols=c(formatted_raw_est, formatted_std_est), 
               names_to = "Estimate_Type", 
               values_to = "Estimate")%>%
  pivot_wider(
    names_from = c(lhs, Estimate_Type),
    values_from = Estimate,
    names_sep = "_")

#Combine results, rename rhs
combined_vent_html<- rbind(dim_vent_html, tails_vent_html, matched_vent_html)%>%
  mutate(rhs = recode(rhs, "vent" = "CSF", "age" = "Age", "sex" = "Sex", "site_id" = "Site ID", "puberty_stage" = "Pubertal Stage", 
                      "ethnicity" = "Ethnicity", "race_3" = "Race", "parent_education" = "Parental Education", "combined_income" = "Combined Income"))

#Create a formatted regression table 
vent_regression_table <- combined_vent_html %>%
  gt(groupname_col = "model", rowname_col = "rhs") %>%
  tab_header(
    title = "Table X. Regression results for models predicting cognitive outcomes using cGM across 3 modeling frameworks, controlling for covaraites",
    subtitle = "Raw and Standardized Estimates"
  ) %>%
  cols_label(
    nihtbx_picvocab_uncorrected_formatted_raw_est = "Raw", nihtbx_picvocab_uncorrected_formatted_std_est = "Standardized",
    nihtbx_flanker_uncorrected_formatted_raw_est = "Raw", nihtbx_flanker_uncorrected_formatted_std_est = "Standardized",
    nihtbx_list_uncorrected_formatted_std_est = "Raw", nihtbx_list_uncorrected_formatted_std_est = "Standardized",
    nihtbx_cardsort_uncorrected_formatted_raw_est = "Raw", nihtbx_cardsort_uncorrected_formatted_std_est = "Standardized",
    nihtbx_pattern_uncorrected_formatted_raw_est = "Raw", nihtbx_pattern_uncorrected_formatted_std_est = "Standardized",
    nihtbx_picture_uncorrected_formatted_raw_est = "Raw", nihtbx_picture_uncorrected_formatted_std_est = "Standardized", 
    nihtbx_reading_uncorrected_formatted_raw_est = "Raw", nihtbx_reading_uncorrected_formatted_std_est = "Standardized"
  ) %>%
  tab_spanner(
    label = "Language",
    columns = c(nihtbx_picvocab_uncorrected_formatted_raw_est, nihtbx_picvocab_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Inhibitory Control",
    columns = c(nihtbx_flanker_uncorrected_formatted_raw_est, nihtbx_flanker_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Cognitive Flexibility",
    columns = c(nihtbx_list_uncorrected_formatted_raw_est, nihtbx_list_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Working Memory",
    columns = c(nihtbx_cardsort_uncorrected_formatted_raw_est, nihtbx_cardsort_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Processing Speed",
    columns = c(nihtbx_pattern_uncorrected_formatted_raw_est, nihtbx_pattern_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Episodic Memory",
    columns = c(nihtbx_picture_uncorrected_formatted_raw_est, nihtbx_picture_uncorrected_formatted_std_est)
  ) %>%
  tab_spanner(
    label = "Reading",
    columns = c(nihtbx_reading_uncorrected_formatted_raw_est, nihtbx_reading_uncorrected_formatted_std_est)
  ) %>%
  row_group_order(groups = c("Dimensional Models", "Tail-Sampled Models", "Propensity Matched Models")) # Order models if necessary

# Save the table as an HTML file
#vent_regression_table %>%
  #gtsave("FINAL_REGRESSION_TABLES/HTML/cog_vent_table.html")
```


And finally, add ALL beta's and p's together in one file to make the heat map: 
```{r}
matched_GMV_fdr<- as.data.frame(matched_GMV_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "GMV")

matched_WMV_fdr<- as.data.frame(matched_WMV_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "WMV")

matched_sGMV_fdr<- as.data.frame(matched_sGMV_fdr)%>%
  filter(rhs == "group")%>% 
  mutate(rhs = "sGMV")

matched_vent_fdr<- as.data.frame(matched_vent_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "Ventricles")

dim_GMV_fdr<- as.data.frame(dim_GMV_fdr)%>%
  filter(rhs == "GMV")

dim_WMV_fdr<- as.data.frame(dim_WMV_fdr)%>%
  filter(rhs == "WMV")

dim_sGMV_fdr<- as.data.frame(dim_sGMV_fdr)%>%
  filter(rhs == "sGMV")

dim_vent_fdr<- as.data.frame(dim_vent_fdr)%>%
  filter(rhs == "Ventricles")

tails_GMV_fdr<- as.data.frame(tails_GMV_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "GMV")

tails_WMV_fdr<- as.data.frame(tails_WMV_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "WMV")

tails_sGMV_fdr<- as.data.frame(tails_sGMV_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "sGMV")

tails_vent_fdr<- as.data.frame(tails_vent_fdr)%>%
  filter(rhs == "group")%>%
  mutate(rhs = "Ventricles")


all_cog<-rbind(matched_GMV_fdr, matched_WMV_fdr, matched_sGMV_fdr, matched_vent_fdr, dim_GMV_fdr, dim_WMV_fdr, dim_sGMV_fdr, dim_vent_fdr, tails_GMV_fdr, 
                tails_WMV_fdr, tails_sGMV_fdr, tails_vent_fdr)

box_write(all_cog, file_name = 'all_cog_stats_UNSCALED_10.21.24.csv', dir_id = '203279384208')
```