---
title: "Step 01: Match on Centiles"
output:
  html_document:
    df_print: paged
---

This R Notebook includes steps taken to create tail-sampled and matched data sets for cGM, sGM, WM, and CSF tissues in ABCD. 

------------------------------
Set Up
------------------------------

First, install necessary packages.
```{r}
library(MatchIt)
library(boxr)
library(tidyr)
library(dplyr)
library(cobalt)
library(ggplot2)
library(finalfit)
library(Hmisc)
library(tidyverse)
library(rstatix)
library(ggpubr)
```

Specify that select function should be pulled from dplyr
```{r}
ggarrange<- ggpubr::ggarrange
select <- dplyr::select
`%ni%` = Negate(`%in%`)
```

Next, log into PennBox, and set working directory the project directory.
```{r}
box_auth()

box_setwd('203279384208')
```
Read in Structural Data/ motion measure, and add to data
```{r}
centiles<- box_read('1267779812594', fread=T)
centiles$participant<-gsub('sub-NDARINV','NDAR_INV',centiles$participant)

centiles<- rename(centiles, src_subject_id = participant)%>%
  select(-sex, -site)

euler<-box_read('1314622137417', fread=TRUE)
euler$id<-gsub('sub-NDARINV','NDAR_INV',euler$id)
euler<- rename(euler, src_subject_id = id)
```

Read in data for propensity matching
```{r}
matching_data<- box_read('1495378893408')
```

Filter for participants with acceptable imaging data, create a age+sex interaction term
Drop cases with incomplete data on matching variables 
```{r}
data_clean<-matching_data%>%
  filter(imgincl_t1w_include == 1)%>%
  filter(imgincl_t2w_include == 1)%>%
  mutate(age_by_sex=(demo_sex_v2*demo_brthdat_v2))%>%
  drop_na(site_id_l, demo_brthdat_v2, demo_sex_v2, demo_prnt_ed_v2, demo_comb_income_v2, demo_ethn_v2, 
          race3, pds_y_ss, euler) 
```

Rename variables for clarity.
```{r}
cols<-colnames(data_clean)
cols
```

```{r}
cols2<- c('subjectkey', 'site_id', 'family', 'GMV', 'WMV', 'sGMV', 'Ventricles', 'age', 'eventname', 'sex', 
          'parent_education', 'combined_income', 'ethnicity', 'race_3', 'puberty_stage', 't1w_inc', 't2w_inc',
          'euler', 'age_by_sex')
          
data_clean2<-data_clean %>%
  rename_at(all_of(cols), ~cols2)
```

------------------------------
Create Tailed Sampled Data
------------------------------

randomly select one sibling per family 
```{r}
set.seed(12345) 

data_clean_no_sibs <-data_clean2 %>% group_by(family) %>% slice_sample(n = 1) %>%  ungroup() 
```

Check distributions and save means and mads for indexing
```{r}
data_clean_no_sibs%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  hist.data.frame()

data_clean_no_sibs%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  psych::describe()

mads<-data_clean_no_sibs%>%
  select(GMV, WMV, sGMV, Ventricles)%>%
  psych::describe()%>%
  as_tibble()%>%
  select(mean, median, mad)%>%
  as.data.frame()

rownames(mads)<-c('GMV','WMV','sGMV','Ventricles')
```

Save unmatched data for comparison. First, keep dimensional network sizes. 
```{r}
#box_write(data_clean_no_sibs, file_name='unmatched_dimensional_data.02.07.24.csv', dir_id='218960591983')
```


Calculate high/low values and create group variable for each network (high= 1, treatment; low= 0, control), using p's one MAD above/below median (look in the tails). 
```{r}
high1<- filter(data_clean_no_sibs, GMV>(mads[1,2]+mads[1,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low1<- filter(data_clean_no_sibs, GMV<(mads[1,2]-mads[1,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
GMV<-rbind(high1, low1)

high2<- filter(data_clean_no_sibs, WMV>(mads[2,2]+mads[2,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low2<- filter(data_clean_no_sibs, WMV<(mads[2,2]-mads[2,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
WMV<-rbind(high2, low2)

high3<- filter(data_clean_no_sibs, sGMV>(mads[3,2]+mads[3,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low3<- filter(data_clean_no_sibs, sGMV<(mads[3,2]-mads[3,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
sGMV<-rbind(high3, low3)

high4<- filter(data_clean_no_sibs, Ventricles>(mads[4,2]+mads[4,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
low4<- filter(data_clean_no_sibs, Ventricles<(mads[4,2]-mads[4,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
Vent<-rbind(high4, low4)
```

merge each network group with clean data for matching
```{r}
GMV<-merge(GMV, data_clean_no_sibs)
WMV<-merge(WMV, data_clean_no_sibs) 
sGMV<-merge(sGMV, data_clean_no_sibs)
Vent<-merge(Vent, data_clean_no_sibs)
```

write out median +/- 1 MAD split data. 
```{r}
#box_write(GMV, file_name='MAD_split_gmv_data_02.07.24.csv', dir_id='218960591983')
#box_write(WMV, file_name='MAD_split_wmv_data_02.07.24.csv', dir_id='218960591983')
#box_write(sGMV, file_name='MAD_split_sgmv_data_02.07.24.csv', dir_id='218960591983')
#box_write(Vent, file_name='MAD_split_vent_data_02.07.24.csv', dir_id='218960591983')
```


------------------------------
Create Matched Data
------------------------------

Set labels for Loveplots:
```{r}
new.labels=c(distance = 'Distance', 
             age = 'Age',
             sex_2 = 'Sex', 
             age_by_sex = 'Age x Sex',
             site_id = 'Site ID', 
             puberty_stage = 'Puberty Stage', 
             ethnicity_2 = 'Ethnicity', 
             race_3 = 'Race', 
             parent_education = 'Parent Education', 
             combined_income = 'Combined Income', 
             euler = 'Motion (Euler)')
```

Match each measure:

GMV:
```{r}
match_GMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 + 
                      parent_education + combined_income + euler,
                     data = GMV,  method = "nearest", caliper=0.1, distance = "glm")

summary(match_GMV) 
plot(summary(match_GMV))
gmv_high_plot<- love.plot(match_GMV,  binary = "std", thresholds = c(m = .1), 
                          var.names = new.labels)

match_GMV_data <- match.data(match_GMV)
#box_write(match_GMV_data, file_name='match_GMV_data_treat_high_02.07.24.csv', dir_id='218960591983')
```

WMV: 
```{r}
match_WMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 + 
                      parent_education + combined_income + euler,
                     data = WMV, method = "nearest", caliper=0.1, distance = "glm")

summary(match_WMV)
plot(summary(match_WMV))
wmv_high_plot<- love.plot(match_WMV,  binary = "std", thresholds = c(m = .1),
                          var.names = new.labels)


match_WMV_data <- match.data(match_WMV)
#box_write(match_WMV_data, file_name='match_WMV_data_treat_high_02.07.24.csv', dir_id='218960591983')
```
sGMV: 
```{r}
match_sGMV <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 + 
                      parent_education + combined_income + euler,
                     data = sGMV,  method = "nearest", caliper=0.1,distance = "glm")

summary(match_sGMV)
plot(summary(match_sGMV))
sgmv_high_plot<- love.plot(match_sGMV,  binary = "std", thresholds = c(m = .1),
                           var.names = new.labels)


match_sGMV_data <- match.data(match_sGMV)
#box_write(match_sGMV_data, file_name='match_sGMV_data_treat_high_02.07.24.csv', dir_id='218960591983')
```

Vent: 
```{r}
match_vent <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 + 
                      parent_education + combined_income + euler,
                     data = Vent, caliper=0.1, method = "nearest", distance = "glm")

summary(match_vent)
plot(summary(match_vent))
vent_high_plot<- love.plot(match_vent,  binary = "std", thresholds = c(m = .1),
                           var.names = new.labels)


match_vent_data <- match.data(match_vent)
#box_write(match_vent_data, file_name='match_vent_data_treat_high_02.07.24.csv', dir_id='218960591983')
```

Redo based with re-assigned treatment and control groups (ie: low=1, high=0)

Calculate high/low values and create group variable for each tissue type:
```{r}
high1<- filter(data_clean_no_sibs, GMV>(mads[1,2]+mads[1,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low1<- filter(data_clean_no_sibs, GMV<(mads[1,2]-mads[1,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
GMV_2<-rbind(high1, low1)

high2<- filter(data_clean_no_sibs, WMV>(mads[2,2]+mads[2,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low2<- filter(data_clean_no_sibs, WMV<(mads[2,2]-mads[2,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
WMV_2<-rbind(high2, low2)

high3<- filter(data_clean_no_sibs, sGMV>(mads[3,2]+mads[3,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low3<- filter(data_clean_no_sibs, sGMV<(mads[3,2]-mads[3,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
sGMV_2<-rbind(high3, low3)

high4<- filter(data_clean_no_sibs, Ventricles>(mads[4,2]+mads[4,3]))%>%
  mutate(group=0)%>%
  select(subjectkey, group)
low4<- filter(data_clean_no_sibs, Ventricles<(mads[4,2]-mads[4,3]))%>%
  mutate(group=1)%>%
  select(subjectkey, group)
Vent_2<-rbind(high4, low4)
```

merge each tissue group with clean data for matching
```{r}
GMV_2<-merge(GMV_2, data_clean_no_sibs)
WMV_2<-merge(WMV_2, data_clean_no_sibs) 
sGMV_2<-merge(sGMV_2, data_clean_no_sibs)
Vent_2<-merge(Vent_2, data_clean_no_sibs)
```

and match each tissue type:

GMV:
```{r}
match_GMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                         parent_education + combined_income + euler, 
                     data = GMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_GMV_2)
plot(summary(match_GMV_2))
gmv_low_plot<- love.plot(match_GMV_2,  binary = "std", thresholds = c(m = .1),
                         var.names = new.labels)

match_GMV_data_2 <- match.data(match_GMV_2)
#box_write(match_GMV_data_2, file_name='match_GMV_data_treat_low_02.07.24.csv', dir_id='218960591983')
```

WMV: 
```{r}
match_WMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                         parent_education + combined_income+ euler, 
                     data =  WMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_WMV_2)
plot(summary(match_WMV_2))
wmv_low_plot<- love.plot(match_WMV_2,  binary = "std", thresholds = c(m = .1),
                         var.names = new.labels)

match_WMV_data_2 <- match.data(match_WMV_2)
#box_write(match_WMV_data_2, file_name='match_WMV_data_treat_low_02.07.24.csv', dir_id='218960591983')
```

sGMV:
```{r}
match_sGMV_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                          parent_education + combined_income+ euler, 
                     data =  sGMV_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_sGMV_2)
plot(summary(match_sGMV_2))
sgmv_low_plot<- love.plot(match_sGMV_2,  binary = "std", thresholds = c(m = .1),
                          var.names = new.labels)

match_sGMV_data_2 <- match.data(match_sGMV_2)
#box_write(match_sGMV_data_2, file_name='match_sGMV_data_treat_low_02.07.24.csv', dir_id='218960591983')
```

Vent: 
```{r}
match_vent_2 <- matchit(group ~ age + sex + age_by_sex + site_id + puberty_stage + ethnicity + race_3 +
                          parent_education + combined_income+ euler, 
                     data =  Vent_2, caliper=0.1, method = "nearest", distance = "glm")

summary(match_vent_2)
plot(summary(match_vent_2))
vent_low_plot<- love.plot(match_vent_2,  binary = "std", thresholds = c(m = .1),
                          var.names = new.labels)

match_vent_data_2 <- match.data(match_vent_2)
#box_write(match_vent_data_2, file_name='match_vent_data_treat_low_02.07.24.csv', dir_id='218960591983')
```

Check overlap between samples for each measure on high/low (ie: are the target high participants the same as the people who were pulled to match the target low participants)

GMV (target=high)
```{r}
gmv_target_high<- filter(match_GMV_data, group==1)
gmv_match_high<- filter(match_GMV_data_2, group==0)

high_gmv_ids<-(intersect(gmv_target_high$subjectkey ,gmv_match_high$subjectkey))
high_gmv<-filter(match_GMV_data, subjectkey %in% high_gmv_ids)
```

GMV (target=low)
```{r}
gmv_target_low<- filter(match_GMV_data_2, group==1)
gmv_match_low<- filter(match_GMV_data, group==0)

low_gmv_ids<-(intersect(gmv_target_low$subjectkey ,gmv_match_low$subjectkey))
low_gmv<-filter(match_GMV_data, subjectkey %in% low_gmv_ids)
```

all gmv:
```{r}
match_gmv<- rbind(high_gmv, low_gmv)
#box_write(match_gmv, file_name='match_gmv_data_overlap_02.07.24.csv', dir_id='218960591983')
```

WMV (target=high)
```{r}
wmv_target_high<- filter(match_WMV_data, group==1)
wmv_match_high<- filter(match_WMV_data_2, group==0)

high_wmv_ids<-(intersect(wmv_target_high$subjectkey ,wmv_match_high$subjectkey))
high_wmv<-filter(match_WMV_data, subjectkey %in% high_wmv_ids)
```

WMV (target=low)
```{r}
wmv_target_low<- filter(match_WMV_data_2, group==1)
wmv_match_low<- filter(match_WMV_data, group==0)

low_wmv_ids<-(intersect(wmv_target_low$subjectkey ,wmv_match_low$subjectkey))
low_wmv<-filter(match_WMV_data, subjectkey %in% low_wmv_ids)
```

all wmv:
```{r}
match_wmv<- rbind(high_wmv, low_wmv)
#box_write(match_wmv, file_name='match_wmv_data_overlap_02.07.24.csv', dir_id='218960591983')
```

sGMV (target=high)
```{r}
sgmv_target_high<- filter(match_sGMV_data, group==1)
sgmv_match_high<- filter(match_sGMV_data_2, group==0)

high_sgmv_ids<-(intersect(sgmv_target_high$subjectkey ,sgmv_match_high$subjectkey))
high_sgmv<-filter(match_sGMV_data, subjectkey %in% high_sgmv_ids)
```

sGMV (target=low)
```{r}
sgmv_target_low<- filter(match_sGMV_data_2, group==1)
sgmv_match_low<- filter(match_sGMV_data, group==0)

low_sgmv_ids<-(intersect(sgmv_target_low$subjectkey ,sgmv_match_low$subjectkey))
low_sgmv<-filter(match_sGMV_data, subjectkey %in% low_sgmv_ids)
```

all sgmv:
```{r}
match_sgmv<- rbind(high_sgmv, low_sgmv)
#box_write(match_sgmv, file_name='match_sgmv_data_overlap_02.07.24.csv', dir_id='218960591983')
```

vent (target=high)
```{r}
vent_target_high<- filter(match_vent_data, group==1)
vent_match_high<- filter(match_vent_data_2, group==0)

high_vent_ids<-(intersect(vent_target_high$subjectkey ,vent_match_high$subjectkey))
high_vent<-filter(match_vent_data, subjectkey %in% high_vent_ids)
```

vent (target=low)
```{r}
vent_target_low<- filter(match_vent_data_2, group==1)
vent_match_low<- filter(match_vent_data, group==0)

low_vent_ids<-(intersect(vent_target_low$subjectkey ,vent_match_low$subjectkey))
low_vent<-filter(match_vent_data, subjectkey %in% low_vent_ids)
```

all vent:
```{r}
match_vent<- rbind(high_vent, low_vent)
#box_write(match_vent, file_name='match_vent_data_overlap_02.07.24.csv', dir_id='218960591983')
```

Who did we kick out? 
```{r}
n_high_gmv<- filter(GMV, group==1)
n_low_gmv<- filter(GMV, group==0)
n_high_gmv_MATCH<- filter(match_gmv, group==1)
n_low_gmv_MATCH<- filter(match_gmv, group==0)

n_high_wmv<- filter(WMV, group==1)
n_low_wmv<- filter(WMV, group==0)
n_high_wmv_MATCH<- filter(match_wmv, group==1)
n_low_wmv_MATCH<- filter(match_wmv, group==0)

n_high_sgmv<- filter(sGMV, group==1)
n_low_sgmv<- filter(sGMV, group==0)
n_high_sgmv_MATCH<- filter(match_sgmv, group==1)
n_low_sgmv_MATCH<- filter(match_sgmv, group==0)

n_high_vent<- filter(Vent, group==1)
n_low_vent<- filter(Vent, group==0)
n_high_vent_MATCH<- filter(match_vent, group==1)
n_low_vent_MATCH<- filter(match_vent, group==0)
```

Make giant plot with all love plots
```{r}
gmv_plots<- ggarrange(gmv_high_plot, gmv_low_plot, nrow=1, ncol=2,
                      common.legend=T)
wmv_plots<- ggarrange( wmv_high_plot, wmv_low_plot, nrow=1, ncol=2,
                       common.legend=T) 
sgmv_plots<-ggarrange(sgmv_high_plot, sgmv_low_plot, nrow=1, ncol=2,
                      common.legend=T) 
vent_plots<- ggarrange(vent_high_plot, vent_low_plot, nrow=1, ncol=2, 
                       common.legend=T)
```

------------------------------
Check Missingness
------------------------------

Organize:
```{r}
missing_data<- filter(matching_data, src_subject_id %ni% data_clean$subjectkey)%>%
  mutate(group=as.factor(1))%>%
  select(src_subject_id, group, GMV, WMV, sGMV, Ventricles)

have_data<- mutate(data_clean, group=as.factor(0))%>%
  select(src_subject_id, group, GMV, WMV, sGMV, Ventricles)

check_missing_data<- rbind(missing_data, have_data)
```

Test:
```{r}
t.test(GMV~group, data=check_missing_data)
eff_gmv<- cohens_d(GMV~group, data=check_missing_data)
t.test(WMV~group, data=check_missing_data)
eff_wmv<- cohens_d(WMV~group, data=check_missing_data)
t.test(sGMV~group, data=check_missing_data) 
eff_sGMV<- cohens_d(sGMV~group, data=check_missing_data) 
t.test(Ventricles~group, data=check_missing_data)
eff_vent<-cohens_d(Ventricles~group, data=check_missing_data)
```

Plot: 
```{r}
missing_gmv<-ggplot(check_missing_data, aes(y=GMV, x=as.factor(group), fill=as.factor(group))) +
  geom_boxplot() +
  stat_compare_means(method="t.test", 
                     label.y = 1.16) + labs(x="", y="cGM", fill="Group")  + theme_classic() +
  scale_x_discrete(labels = c("Incomplete Data", "Complete Data")) +
  annotate("text", x='0', y=1.2, 
           label =  paste("Cohen's d =", round(eff_gmv$effsize, 2)),
           color = "black", size = 4) +
  scale_fill_manual(values=c("#F8766D", "#00BFC4")) +
  theme(legend.position="none") 

missing_gmv

missing_wmv<-ggplot(check_missing_data, aes(y=WMV, x=as.factor(group), fill=as.factor(group) )) + geom_boxplot() +
  stat_compare_means(method="t.test",
                     label.y = 1.16) +  labs(x="", y="WM", fill="Group")  + theme_classic() +
  scale_fill_manual(values=c("#F8766D", "#00BFC4")) +
  annotate("text", x='0', y=1.2, 
           label =  paste("Cohen's d =", round(eff_wmv$effsize, 2)),
           color = "black", size = 4) +
  scale_x_discrete(labels = c("Incomplete Data", "Complete Data")) +
  theme(legend.position="none")

missing_wmv

missing_sgmv<-ggplot(check_missing_data, aes(y=sGMV, x=as.factor(group), fill=as.factor(group) )) + geom_boxplot() +
  stat_compare_means(method="t.test",
                     label.y = 1.16) + labs(x="", y="sGM", fill="Group") + theme_classic() +
  scale_fill_manual(values=c("#F8766D", "#00BFC4")) +
  annotate("text", x='0', y=1.2, 
           label =  paste("Cohen's d =", round(eff_sGMV$effsize, 2)),
           color = "black", size = 4) +
  scale_x_discrete(labels = c("Incomplete Data", "Complete Data")) +
  theme(legend.position="none")

missing_sgmv

missing_vent<-ggplot(check_missing_data, aes(y=Ventricles, x=as.factor(group), fill=as.factor(group) )) + geom_boxplot() +
  stat_compare_means(method="t.test",
                     label.y = 1.16) + labs(x="", y="CSF", fill="Group") + theme_classic() +
  scale_fill_manual(values=c("#F8766D", "#00BFC4")) +
  annotate("text", x='0', y=1.2, 
           label =  paste("Cohen's d =", round(eff_vent$effsize, 2)),
           color = "black", size = 4) +
  scale_x_discrete(labels = c("Incomplete Data", "Complete Data")) +
  theme(legend.position="none")

missing_vent

missing_plots<-ggarrange(missing_gmv,missing_wmv,missing_sgmv,missing_vent, nrow=2, ncol=2)
missing_plots

ggsave(file="missing_plot.svg", plot = missing_plots, width=10, height=8)

```

Check differences in demographics across target/matched groups per measure
high gmv (target=1, match=0)
```{r}
rbind(gmv_target_high, gmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low gmv (target=1, match=0)
```{r}
rbind(gmv_target_low, gmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high wmv (target=1, match=0)
```{r}
rbind(wmv_target_high, wmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low wmv (target=1, match=0)
```{r}
rbind(wmv_target_low, wmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high sgmv (target=1, match=0)
```{r}
rbind(sgmv_target_high, sgmv_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low sgmv (target=1, match=0)
```{r}
rbind(sgmv_target_low, sgmv_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

high vent (target=1, match=0)
```{r}
rbind(vent_target_high, vent_match_high)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```

low vent (target=1, match=0)
```{r}
rbind(vent_target_low, vent_match_low)%>%
  select(-c(distance, weights, subclass))%>%
  pivot_longer(-c(group, subjectkey), names_to = 'variables', values_to = 'value')%>%
  group_by(variables) %>%
  t_test(value ~ group) %>%
  adjust_pvalue(method = "BH") %>%
  add_significance()
```
